### 2014-05-29 abstract.tex
Initial, from Authorea

Recently, an object detection architecture based on two key decisions
has demonstrated an undeniable increase in performance on both PASCAL
VOC and ILSVRC detection datasets. The first is doing bottom-up Region
of Interest (ROI) proposals instead of sliding-window evaluation. The
second is using multi-layer Convolutional Neural Nets (CNNs) pre-trained
on ILSVRC classification data to featurize canonically resized ROIs.
Although by far the best in terms of recognition performance, the method
is computationally costly, requiring processing of several hundred of
thousand regions with the CNN. Even with efficient GPU implementation,
the method takes \textasciitilde{}10 s per image after the computation
of region proposals (another \textasciitilde{}2 s).

We propose three novel speed-ups for the task. (1) Dense evaluation: the
whole image is processed with a CNN up to the highest
non-fully-connected layer, and ROIs are featurized by cropping and
resizing that highest layer, for use as an initial filter. (2) Cascaded
CNN: each ROI passing the initial filter is further processed by a CNN
that is augmented with a \emph{reject} option after each layer. (3) The
selection of ROIs for further processing is done dynamically, taking
into account the evaluation results on the ROIs selected so far.

Combined, these speed-ups allow us to match original R-CNN performance
in 20\% of the time.

### 2014-05-29 conclusion.tex
Initial, from Authorea

\section{Conclusion}\label{conclusion}

{[}Standard stuff{]}

\subsection{Future work}\label{future-work}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  ?
\end{itemize}

### 2014-05-29 evaluation.tex
Initial, from Authorea

\section{Evaluation}\label{evaluation}

(All results are on PASCAL VOC 2007 and 2010. ILSVRC is nice-to-have.)

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  {[}TABLE: Dense region evaluation, timing vs.~accuracy: effect of
  multi scale, pooling.{]}
\item
  From the above, we select the point of high accuracy and reasonable
  cost.
\item
  {[}PLOT: Cascaded CNN timing vs.~accuracy: effect of threshold.{]}
\item
  From the above, we select threshold of high accuracy and reasonable
  cost.
\item
  {[}TABLE: Combined system timing vs accuracy: effect of dynamic region
  selection.{]}
\end{itemize}

### 2014-05-29 introduction.tex
Initial, from Authorea

\section{Introduction}\label{introduction}

{[}Standard object detection, deep learning, computational concerns,
introduction{]}

### 2014-05-29 method.tex
Initial, from Authorea

\section{Method}\label{method}

Our method builds on the architecture described in R-CNN.

{[}FIGURE: R-CNN schematic, for contrast with the next figure{]}

\subsection{Dense region evaluation}\label{dense-region-evaluation}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Explain the difference between cropping pixels and cropping
  \texttt{pool5}.
\item
  Explain design choices (single vs multi scale, finding nearest window,
  warping.
\item
  {[}FIGURE: dense region evaluation: multi-scale pyramid, warping{]}
\end{itemize}

\subsection{Cascaded CNN}\label{cascaded-cnn}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Explain the reject option in the CNN evaluation
\item
  Each rejector is trained to distiguish background regions from
  foreground (object) regions.
\item
  Explain training the thresholds
\item
  {[}FIGURE: Cascaded CNN, showing threshold layers{]}
\end{itemize}

\subsection{Dynamic region selection}\label{dynamic-region-selection}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Explain dynamic selection of region batches
\item
  Explain iterative training procedure
\item
  {[}FIGURE: dynamic region selection loop, updating region features{]}
\end{itemize}

\subsection{Combined system}\label{combined-system}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Explain how the components fit together
\item
  {[}FIGURE: schematic of the parts fitting together{]}
\end{itemize}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
\caption{R-CNN architecture: image regions are cropped, resized, and each one fed
through a CNN with classification layers. The classifier outputs are
post-processed to give the final detections.
}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
\caption{Dense R-CNN architecture: the whole image is fed through a CNN up to the
highest pooling layer. Regions are cropped from that layer, resized, and
classified. The classifier outputs are post-processed to give the final
detections.
}
\end{center}
\end{figure}

### 2014-05-29 related_work.tex
Initial, from Authorea

\section{Related Work}\label{related-work}

\subsubsection{Object recognition with
CNN}\label{object-recognition-with-cnn}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Alexnet
\item
  RCNN and the couple other CNN detection methods
\item
  Overfeat: explain dense evaluation
\end{itemize}

\subsubsection{Cascaded detection}\label{cascaded-detection}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Viola Jones
\item
  Cascaded DPM
\item
  Is there any CNN work?
\end{itemize}

\subsubsection{Dynamic selection}\label{dynamic-selection}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Timely Object Recognition
\item
  Cross-talk cascades
\item
  ?
\end{itemize}

### 2014-05-29 copy_bibtex.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+# Copy the "NIPS" Mendeley group bibtex to this folder.
+
+cp /Users/sergeyk/Dropbox/Documents/Mendeley/NIPS14.bib sergeyk_nips14.bib

### 2014-05-29 method.tex
reworked figures

@@
+%!TEX root=paper.tex
 \section{Method}\label{method}
 
-Our method builds on the architecture described in R-CNN.
+Our method builds on the architecture described in \cite{Girshick2014}, summarized in \autoref{fig:rcnn}.
 
-{[}FIGURE: R-CNN schematic, for contrast with the next figure{]}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
+\caption{
+R-CNN architecture: image regions are cropped, resized, and each one fed through a CNN with classification layers.
+The classifier outputs are post-processed to give the final detections.
+}\label{fig:rcnn}
+\end{center}
+\end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Dense region evaluation}\label{dense-region-evaluation}
+
+\autoref{fig:dense_rcnn} shows the dense region evaluation.
 
@@
 \item
-  Explain the difference between cropping pixels and cropping
-  \texttt{pool5}.
+  Explain the difference between cropping pixels and cropping \texttt{pool5}.
 \item
-  Explain design choices (single vs multi scale, finding nearest window,
-  warping.
-\item
-  {[}FIGURE: dense region evaluation: multi-scale pyramid, warping{]}
+  Explain design choices (single vs multi scale, finding nearest window, warping.
 \end{itemize}
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
+\caption{
+Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
+Regions are cropped from that layer, resized, and classified.
+The classifier outputs are post-processed to give the final detections.
+}\label{fig:dense_rcnn}
+\end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Cascaded CNN}\label{cascaded-cnn}
@@
 \item
-  Each rejector is trained to distiguish background regions from
-  foreground (object) regions.
+  Each rejector is trained to distiguish background regions from foreground (object) regions.
 \item
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Dynamic region selection}\label{dynamic-region-selection}
+
+\autoref{fig:combined} shows the dynamic region selection loop.
 
@@
   Explain iterative training procedure
-\item
-  {[}FIGURE: dynamic region selection loop, updating region features{]}
-\end{itemize}
-
-\subsection{Combined system}\label{combined-system}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Explain how the components fit together
-\item
-  {[}FIGURE: schematic of the parts fitting together{]}
 \end{itemize}
@@
 \begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
-\caption{R-CNN architecture: image regions are cropped, resized, and each one fed
-through a CNN with classification layers. The classifier outputs are
-post-processed to give the final detections.
-}
+\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
+\caption{
+Dynamic region selection combines both speedups and introduces another.
+}\label{fig:combined}
 \end{center}
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
-\caption{Dense R-CNN architecture: the whole image is fed through a CNN up to the
-highest pooling layer. Regions are cropped from that layer, resized, and
-classified. The classifier outputs are post-processed to give the final
-detections.
-}
-\end{center}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Combined system}\label{combined-system}
+
+The entire system is combined by using Dense R-CNN as the fast feature and Cascaded CNN as the region evaluator in \autoref{fig:combined}.

### 2014-05-29 conclusion.tex
reworked figures
Method fleshed out, added gradient section, added references, adjusted figures, added loremipsum placeholder

@@
-\section{Conclusion}\label{conclusion}
+%!TEX root=paper.tex
+\section{Conclusion}\label{sec:conclusion}
 
-{[}Standard stuff{]}
+\todo{Standard stuff}
 
-\subsection{Future work}\label{future-work}
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\subsection{Future work}\label{sec:future}
 
@@
 \item
-  ?
+    \todo{ILSVRC results}
+\item
+    \todo{Training termination layers jointly with the rest of the network.}
 \end{itemize}

### 2014-05-29 evaluation.tex
reworked figures
Method fleshed out, added gradient section, added references, adjusted figures, added loremipsum placeholder

@@
-\section{Evaluation}\label{evaluation}
+%!TEX root=paper.tex
+\section{Evaluation}\label{sec:evaluation}
 
-(All results are on PASCAL VOC 2007 and 2010. ILSVRC is nice-to-have.)
+All results are on PASCAL VOC 2007 and 2010/2012.
 
@@
 \item
-  {[}TABLE: Dense region evaluation, timing vs.~accuracy: effect of
-  multi scale, pooling.{]}
+    \todo{TABLE: Dense region evaluation, timing vs.~accuracy: effect of multi scale, pooling.}
 \item
-  From the above, we select the point of high accuracy and reasonable
-  cost.
+    From the above, we select the point of high accuracy and reasonable cost.
 \item
-  {[}PLOT: Cascaded CNN timing vs.~accuracy: effect of threshold.{]}
+    \todo{Cascaded CNN timing vs.~accuracy: effect of threshold.}
 \item
-  From the above, we select threshold of high accuracy and reasonable
-  cost.
+    From the above, we select threshold of high accuracy and reasonable cost.
 \item
-  {[}TABLE: Combined system timing vs accuracy: effect of dynamic region
-  selection.{]}
+    \todo{TABLE: Combined system timing vs accuracy: effect of dynamic region selection.}
+\item
+    \todo{FIGURE: AP vs time plots}
 \end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2014-05-29 introduction.tex
Method fleshed out, added gradient section, added references, adjusted figures, added loremipsum placeholder

@@
+% !TEX root=paper.tex
 \section{Introduction}\label{introduction}
 
-{[}Standard object detection, deep learning, computational concerns,
-introduction{]}
+\todo{
+Standard object detection, deep learning, computational concerns, introduction.
+}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+We discuss related work in \autoref{sec:related}, cover all parts of our proposed method in \autoref{sec:method}, and present evaluation results on the PASCAL VOC in \autoref{sec:evaluation}.

### 2014-05-29 method.tex
Cascaded CNN figure
Method fleshed out, added gradient section, added references, adjusted figures, added loremipsum placeholder

@@
 %!TEX root=paper.tex
-\section{Method}\label{method}
+\section{Method}\label{sec:method}
 
-Our method builds on the architecture described in \cite{Girshick2014}, summarized in \autoref{fig:rcnn}.
+Our method builds on the architecture described in \cite{Girshick-CVPR-2014}.
+As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and then does the following: (1) for each ROI, classifies it with a CNN, obtaining multi-class scores; (2) post-processes the scored ROIs with non-maximal suppression and other bounding box refinement to obtain the final detections.
+
+We aim to incorporate several speed-ups into a similar architecture.
+As summarized in \autoref{fig:combined}, we start with the same ROI proposals, and then (1) score each proposal with a quick-to-compute feature; (2) select the ROI that is most promising, and score it with a CNN, which is additionally sped up with a cascaded structure; (3-a) either select another ROI, incorporating the scores of the first one into the selection -- or (3b) post-process the ROIs scores so far and exit.
+
+For the quick feature, we consider the CNN pixel gradient in \autoref{sec:gradient} and a ``dense'' R-CNN variant in \autoref{sec:dense}.
+The Cascaded CNN is described in \autoref{sec:ccnn}.
+The dynamic region selection is explained in \autoref{sec:dynamic}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dense region evaluation}\label{dense-region-evaluation}
-
-\autoref{fig:dense_rcnn} shows the dense region evaluation.
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Explain the difference between cropping pixels and cropping \texttt{pool5}.
-\item
-  Explain design choices (single vs multi scale, finding nearest window, warping.
-\end{itemize}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
-\caption{
-Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
-Regions are cropped from that layer, resized, and classified.
-The classifier outputs are post-processed to give the final detections.
-}\label{fig:dense_rcnn}
-\end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Cascaded CNN}\label{cascaded-cnn}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Explain the reject option in the CNN evaluation
-\item
-  Each rejector is trained to distiguish background regions from foreground (object) regions.
-\item
-  Explain training the thresholds
-\item
-  {[}FIGURE: Cascaded CNN, showing threshold layers{]}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dynamic region selection}\label{dynamic-region-selection}
-
-\autoref{fig:combined} shows the dynamic region selection loop.
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Explain dynamic selection of region batches
-\item
-  Explain iterative training procedure
-\end{itemize}
-
 \begin{figure}[h!]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Combined system}\label{combined-system}
+\subsection{CNN pixel gradient computation}\label{sec:gradient}
 
-The entire system is combined by using Dense R-CNN as the fast feature and Cascaded CNN as the region evaluator in \autoref{fig:combined}.
+One fast-to-compute feature we consider for the preliminary featurization of ROIs is the pixel gradient, back-propagated throgh the classifier CNN applied to the whole image.
+This gradient corresponds to a kind of saliency map onto the image \cite{Simonyan-ICLR-2014}, and can therefore be used to evaluate ROIs.
+
+\begin{itemize}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+    \todo{Explain backprop to pixels.}
+\item
+    \todo{Explain how we featurize it: warp each ROI to canonical size and also include overall statistics, then train to classify $>0.3$ overlap with ground truth.}
+\item
+    \todo{FIGURE: shows schematic structure of the flow and gradient saliency maps for a couple of images.}
+\end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Dense region evaluation}\label{sec:dense}
+
+Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
+As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the topmost layer of the CNN at best matching scale, warped to the size that the fully-connected layers can process, and classified.
+This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.
+
+\begin{itemize}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  \todo{Explain design choices (single vs multi scale, finding nearest window, warping.}
+\end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
+\caption{
+Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
+Regions are cropped from that layer at the best matching scale, resized, and classified.
+}\label{fig:dense_rcnn}
+\end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Cascaded CNN}\label{sec:ccnn}
+
+Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
+It would be useful to quickly reject these regions, without expending the full amount of computation on them.
+
+The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Terminate'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to terminate with a classification.
+For our purpose, the terminate layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
+Only the last classification layer output the full multi-class scores.
+
+\begin{itemize}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  \todo{Explain training the thresholds.}
+\end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
+\caption{
+The Cascaded CNN has a reject option after certain layers.
+\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
+}\label{fig:ccnn}
+\end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Dynamic region selection}\label{sec:dynamic}
+
+\autoref{fig:combined} shows the dynamic region selection loop.
+
+\begin{itemize}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  \todo{Explain dynamic selection of region batches.}
+\item
+  \todo{Explain iterative training procedure.}
+\end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2014-05-29 related_work.tex
reworked figures
Method fleshed out, added gradient section, added references, adjusted figures, added loremipsum placeholder

@@
-\section{Related Work}\label{related-work}
+%!TEX root=paper.tex
+\section{Related Work}\label{sec:related}
 
-\subsubsection{Object recognition with
-CNN}\label{object-recognition-with-cnn}
+\paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}
 
@@
 \item
-  Alexnet
+  Alexnet \cite{Krizhevsky-NIPS-2012}
 \item
-  RCNN and the couple other CNN detection methods
+  RCNN \cite{Girshick-CVPR-2014} and the couple other CNN detection methods \cite{Zou-CVPR-2014} \cite{Simonyan-ICLR-2014}.
 \item
-  Overfeat: explain dense evaluation
+  Overfeat: explain dense evaluation \cite{Sermanet-ICLR-2014}
 \end{itemize}
 
-\subsubsection{Cascaded detection}\label{cascaded-detection}
+\paragraph{Cascaded detection}\label{cascaded-detection}
 
@@
 \item
-  Viola Jones
+  Viola Jones \cite{Viola2004}
 \item
-  Cascaded DPM
+  Cascaded DPM \cite{Felzenszwalb-CVPR-2010}
 \item
-  Is there any CNN work?
+  \todo{Is there any CNN work?}
 \end{itemize}
 
-\subsubsection{Dynamic selection}\label{dynamic-selection}
+\paragraph{Dynamic selection}\label{dynamic-selection}
 
@@
 \item
-  Timely Object Recognition
+  Timely Object Recognition \cite{Karayev-NIPS-2012}
 \item
-  Cross-talk cascades
+  Cross-talk cascades \cite{Dollar-ECCV-2012}
 \item
-  ?
+  \todo{What else?}
 \end{itemize}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2014-06-05 method.tex
Pyramid R-CNN subsection

@@
 We aim to incorporate several speed-ups into a similar architecture.
-As summarized in \autoref{fig:combined}, we start with the same ROI proposals, and then (1) score each proposal with a quick-to-compute feature; (2) select the ROI that is most promising, and score it with a CNN, which is additionally sped up with a cascaded structure; (3-a) either select another ROI, incorporating the scores of the first one into the selection -- or (3b) post-process the ROIs scores so far and exit.
+As summarized in \autoref{fig:combined}, we start with the same ROI proposals, and then (1) score each proposal with a quick-to-compute feature; (2) select the ROI that is most promising, and score it with a CNN, which is additionally sped up with a cascaded structure; (3a) either select another ROI, incorporating the scores of the first one into the selection -- or (3b) post-process the ROIs scored so far and exit.
 
-For the quick feature, we consider the CNN pixel gradient in \autoref{sec:gradient} and a ``dense'' R-CNN variant in \autoref{sec:dense}.
+For the quick feature, we consider the CNN pixel gradient in \autoref{sec:gradient} and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
 The Cascaded CNN is described in \autoref{sec:ccnn}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dense region evaluation}\label{sec:dense}
+\subsection{Pyramid amortized R-CNN}\label{sec:dense}
 
 Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
-As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the topmost layer of the CNN at best matching scale, warped to the size that the fully-connected layers can process, and classified.
+We call this multiscale CNN output a ``feature pyramid''.
+As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the feature pyramid at the best matching scale, warped to a canonical size, and classified.
+ROIs are highly overlapping, but their featurization is shared through the pyramid, amortizing its construction cost.
 This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.
+
+\subsubsection{Design choices}
+
+We explored a variety of choices while designing Pyramid R-CNN.
+We tried using a single scale or a pyramid with 7 levels each separated by a scale factor of $2^{-1/2}$.
+For warping, we experimented with canonical sizes of $s \times s$, for $s \in \{5,6,7\}$ and resampling with nearest neighbor or bilinear interpolation.
+We also tried two variants of the feature pyramid: the raw feature pyramid or one where each level is max pooled with a $3 \times 3$ pooling window run at a stride of $1$ (to avoid subsampling).
+
+Table ??? shows mAP performance on PASCAL VOC 2007 test for these various choices.
+The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
+The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
+The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
+Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.
+
+To map a ROI $R$ into the pyramid, we start by computing an ``optimal'' scale defined by $\alpha^* = 227/\min(h,w)$, where $h$ and $w$ are image height and width of $R$.
+We then find the nearest level in the pyramid: $l^* = \textrm{argmin}_l |\log(\alpha_l) - \log(\alpha^*)|$, where $\alpha_l$ is the scale factor for pyramid level $l$.
+This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.
 
@@
 \item
-  \todo{Explain design choices (single vs multi scale, finding nearest window, warping.}
+  %\todo{Explain design choices (single vs multi scale, finding nearest window, warping.}
+  \todo{Add table}
 \end{itemize}
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+%\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

### 2014-06-05 introduction.tex
added trevor's intro draft

--- 2014-05-29 introduction.tex
@@
+% !TEX root=paper.tex
 \section{Introduction}\label{introduction}
 
-{[}Standard object detection, deep learning, computational concerns,
-introduction{]}
+Multi-layered convolutional models have recently been shown to offer impressive levels of performance on visual detection tasks, by applying deep convnet models trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
+While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.
+
+Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
+Overfeat overcomes this by incrementally computing the convnet features in overlapping windows, but then restricts the window locations to be on a relatively regular grid.
+RCNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
+While RCNN has leading performance on PASCAL and ImageNet Detection as of the date of this writing, it is rather slow, at XXs per image.
+
+Existing detection schemes, including RCNN and Overfeat, are generally relatively naive in terms of the temporal properties of their inference.
+They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
+In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
+(Or when time is considered a costly resource).
+We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.
+
+Our model yields novel forms of ``cascaded''-style processing for such detectors, where large amounts of computation is pruned when it is deemed redundant, or likely unproductive.
+We consider both static and dynamic policies for such behavior, and features based on low-level cues and mid-level convnet features.
+We focus on speeding up the RCNN framework, but our work is relevant to any detector that operates a relatively expensive function over a set of candidate locations.
+Our model implicily learns to look elsewhere when a nearby region is already examined, and to look above a motorbike for a possible person; it generalized well known principles of non-maximal suppression and inter-task context.
+
+We consider three specific mechanisms, which are independently and jointly valuable.
+[[ 1) dense eval.; 2) cascade; 3) dynamic ]].
+Together we call these ``Timely'' methods for object detection, hence the title of our paper.
+
+We discuss related work in \autoref{sec:related}, cover all parts of our proposed method in \autoref{sec:method}, and present evaluation results on the PASCAL VOC in \autoref{sec:evaluation}.

### 2014-06-06 related_work.tex
initial commit on related work

@@
 \paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Alexnet \cite{Krizhevsky-NIPS-2012}
-\item
-  RCNN \cite{Girshick-CVPR-2014} and the couple other CNN detection methods \cite{Zou-CVPR-2014} \cite{Simonyan-ICLR-2014}.
-\item
-  Overfeat: explain dense evaluation \cite{Sermanet-ICLR-2014}
-\end{itemize}
+The recent success of deep convolutional neural networks (CNN) Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has spurred various investigations \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} how this success can be carried over to an detection task despite the prohibitive cost of evaluating such models densely in a naive manner.
+These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014} as well as deriving a window sampling scheme that is based on the gradient of the network \cite{Simonyan-ICLR-2014}.
+All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
 
 \paragraph{Cascaded detection}\label{cascaded-detection}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  Viola Jones \cite{Viola2004}
-\item
-  Cascaded DPM \cite{Felzenszwalb-CVPR-2010}
-\item
-  \todo{Is there any CNN work?}
-\end{itemize}
+Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order to features/classifiers.
+This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}.
+Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}.
+While previous cascade schemes really on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.
 
 \paragraph{Dynamic selection}\label{dynamic-selection}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
   Timely Object Recognition \cite{Karayev-NIPS-2012}
-\item
   Cross-talk cascades \cite{Dollar-ECCV-2012}
-\item
-  \todo{What else?}
-\end{itemize}
 

### 2014-06-06 related_work.tex
lirum larum

@@
   Cross-talk cascades \cite{Dollar-ECCV-2012}
-
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
-
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

### 2014-06-06 related_work.tex
related

@@
 All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
+In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, we maintain effective canonicalization of region via warping and show its importance for achieving high performance.
 
@@
 \paragraph{Dynamic selection}\label{dynamic-selection}
+Most recently
   Timely Object Recognition \cite{Karayev-NIPS-2012}

### 2014-06-06 related_work.tex
related work

@@
 \paragraph{Cascaded detection}\label{cascaded-detection}
-Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order to features/classifiers.
+Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
 This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}.
 Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}.
-While previous cascade schemes really on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.
+While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.
 
 \paragraph{Dynamic selection}\label{dynamic-selection}
-Most recently
-  Timely Object Recognition \cite{Karayev-NIPS-2012}
-  Cross-talk cascades \cite{Dollar-ECCV-2012}
+Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}.
+We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware.
+In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained dynamic execution policies reasoning on window proposals for more expensive features.

### 2014-06-06 related_work.tex
update on related work

@@
 We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware.
-In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained dynamic execution policies reasoning on window proposals for more expensive features.
+In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.

### 2014-06-06 related_work.tex
fixes

@@
 All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
-In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, we maintain effective canonicalization of region via warping and show its importance for achieving high performance.
+In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Sermanet-ICLR-2014}, we maintain effective canonicalization of region via warping and show its importance for achieving high performance.
 
 \paragraph{Cascaded detection}\label{cascaded-detection}
-Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
+Detection cascades \cite{Viola2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
 This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}.

### 2014-06-06 related_work.tex
updates

@@
 This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}.
-Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}.
+Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade} as well as a boosted cascade trained on CNN features \cite{Zou-CVPR-2014}.
 While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

### 2014-06-06 related_work.tex
updates

@@
 All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
-In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Sermanet-ICLR-2014}, we maintain effective canonicalization of region via warping and show its importance for achieving high performance.
+In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Sermanet-ICLR-2014}, we maintain effective canonicalization of regions and show its importance for achieving high performance.
 

### 2014-06-06 method.tex
added ross' design choices table
adding histogram of # regions per image
results table and figures
Explained the cascaded-CNN a bit more

@@
 
-Table ??? shows mAP performance on PASCAL VOC 2007 test for these various choices.
+\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
 The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
@@
 This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.
+
+\begin{table}[ht]
+\caption{
+    Pyramid R-CNN design choices.
+}\label{tab:prcnn}
+\input{pyra_rcnn_table}
+\end{table}
 
@@
 It would be useful to quickly reject these regions, without expending the full amount of computation on them.
+Since most of the time is spend in the convolution layers, we introduce a reject layer after pool1, pool2, conv3 and conv4, this allows skipping the computation of the following convolutions.
+These reject layers were trained using the corresponding fine-tuned CNN.
 
-The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Terminate'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to terminate with a classification.
-For our purpose, the terminate layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
-Only the last classification layer output the full multi-class scores.
+The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to reject the region since it is background.
+For our purpose, the reject layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
+The last classification layer still outputs the full multi-class scores for the surviving regions.
 
@@
 \caption{
-The Cascaded CNN has a reject option after certain layers.
+The Cascaded CNN has a reject option after pool1, pool2, conv3 and conv4 layers.
 \todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\linewidth]{figures/roi_hist.pdf}
+\caption{
+    Distribution of the number regions per image on PASCAL VOC2007 validation set.
+}\label{fig:roi_hist}
+\end{figure}
+
+\begin{table}[ht]
+\centering
+\caption{
+Full table of AP vs. Time results on PASCAL VOC 2007.
+}\label{tab:results}
+\include{results_table}
+\end{table}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/_speedup.pdf}
+\caption{
+Speedup.
+}\label{fig:speedup}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/_all_selected.pdf}
+\caption{
+AP vs. Time plots.
+}\label{fig:apvst}
+\end{figure}

### 2014-06-06 abstract.tex
abstract

@@
-Recently, an object detection architecture based on two key decisions
-has demonstrated an undeniable increase in performance on both PASCAL
-VOC and ILSVRC detection datasets. The first is doing bottom-up Region
-of Interest (ROI) proposals instead of sliding-window evaluation. The
-second is using multi-layer Convolutional Neural Nets (CNNs) pre-trained
-on ILSVRC classification data to featurize canonically resized ROIs.
-Although by far the best in terms of recognition performance, the method
-is computationally costly, requiring processing of several hundred of
-thousand regions with the CNN. Even with efficient GPU implementation,
-the method takes \textasciitilde{}10 s per image after the computation
-of region proposals (another \textasciitilde{}2 s).
+Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.
+The first point is doing bottom-up Region of Interest (ROI) proposals instead of sliding-window evaluation.
+The second point is using multi-layer Convolutional Neural Nets (CNNs) pre-trained on large-scale classification data to featurize canonically resized ROIs.
+Although state of the art in recognition performance, the method is computationally costly, requiring CNN processing of upwards of two thousand regions.
+Even with efficient GPU implementation, the method takes \textasciitilde{}10 s per image after the computation of region proposals.% (another \textasciitilde{}2 s).
 
-We propose three novel speed-ups for the task. (1) Dense evaluation: the
-whole image is processed with a CNN up to the highest
-non-fully-connected layer, and ROIs are featurized by cropping and
-resizing that highest layer, for use as an initial filter. (2) Cascaded
-CNN: each ROI passing the initial filter is further processed by a CNN
-that is augmented with a \emph{reject} option after each layer. (3) The
-selection of ROIs for further processing is done dynamically, taking
-into account the evaluation results on the ROIs selected so far.
+We propose and evaluate several novel speed-ups for the Region-CNN (R-CNN):
+(1) An initial region filtering step using a ``fast feature,'' with dynamic updates.
+(2) Pyramid R-CNN ``fast feature'': the whole image is processed with a CNN up to the highest
+non-fully-connected layer, from which ROIs are featurized by cropping and resizing.
+(3) Cascaded-CNN: each ROI passing the initial filter is further processed by a CNN that is augmented with a \emph{reject} option after each layer.
 
-Combined, these speed-ups allow us to match original R-CNN performance
-in 20\% of the time.
+We achieve a \textasciitilde{}8x speed-up while losing no more than 10\% of the peak R-CNN detection performance -- or a \textasciitilde{}16x speed-up while losing no more than 20\%.

### 2014-06-06 abstract.tex
done with abstract

@@
+%!TEX root=paper.tex
+\begin{abstract}
 Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.
@@
 Although state of the art in recognition performance, the method is computationally costly, requiring CNN processing of upwards of two thousand regions.
-Even with efficient GPU implementation, the method takes \textasciitilde{}10 s per image after the computation of region proposals.% (another \textasciitilde{}2 s).
+Even with efficient GPU implementation, the method takes \textasciitilde 10 s per image after the computation of region proposals.% (another \textasciitilde 2 s).
 
 We propose and evaluate several novel speed-ups for the Region-CNN (R-CNN):
-(1) An initial region filtering step using a ``fast feature,'' with dynamic updates.
-(2) Pyramid R-CNN ``fast feature'': the whole image is processed with a CNN up to the highest
-non-fully-connected layer, from which ROIs are featurized by cropping and resizing.
-(3) Cascaded-CNN: each ROI passing the initial filter is further processed by a CNN that is augmented with a \emph{reject} option after each layer.
+(1) Initial or ongoing region filtering using one of three ``fast features'': (a) region overlap statistics; (b) CNN pixel gradient statistics; and (c) the \emph{Pyramid R-CNN}, which processes the whole image up to the highest non-fully-connected layer before cropping, resizing, and classifying ROIs.
+(2) \emph{Cascaded CNN}: each ROI passing the initial filter is further processed by a CNN that is augmented with a \emph{reject} option after each layer, allowing much faster but accurate classification.
 
-We achieve a \textasciitilde{}8x speed-up while losing no more than 10\% of the peak R-CNN detection performance -- or a \textasciitilde{}16x speed-up while losing no more than 20\%.
+We achieve a \textasciitilde 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a \textasciitilde 16x speed-up while losing no more than 20\%.
+\end{abstract}

### 2014-06-06 abstract.tex
td comment in abs and minor corrections in intro

@@
 \begin{abstract}
+{\bf TD: this para reads awkward and a bit arrogant to me; can we replace with one crisp and strong sentance?  I also hate two paragraph abstracts.}
 Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.

### 2014-06-06 introduction.tex
td comment in abs and minor corrections in intro

@@
 Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
-Overfeat overcomes this by incrementally computing the convnet features in overlapping windows, but then restricts the window locations to be on a relatively regular grid.
+OverFeat \cite{Sermanet-ICLR-2014} overcomes this by incrementally computing the convnet features in overlapping windows, but then restricts the window locations to be on a relatively regular grid.
 RCNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
@@
 
-Existing detection schemes, including RCNN and Overfeat, are generally relatively naive in terms of the temporal properties of their inference.
+Existing detection schemes, including RCNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
 They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.

### 2014-06-06 evaluation.tex
Removed time 0 ms from table
evaluation figures and some text

--- 2014-05-29 evaluation.tex
@@
-\section{Evaluation}\label{evaluation}
+%!TEX root=paper.tex
+\section{Evaluation}\label{sec:evaluation}
 
-(All results are on PASCAL VOC 2007 and 2010. ILSVRC is nice-to-have.)
+We evaluate on the standard object detection benchmark: the PASCAL VOC \todo{cite?}.
+In all cases, the CNN region classifiers are trained on the PASCAL VOC 2007 trainval set.
+The parameters of our methods are set by training or cross-validation on the VOC 2007 val set.
+We evaluate on the VOC 2007 test set.
 
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  {[}TABLE: Dense region evaluation, timing vs.~accuracy: effect of
-  multi scale, pooling.{]}
-\item
-  From the above, we select the point of high accuracy and reasonable
-  cost.
-\item
-  {[}PLOT: Cascaded CNN timing vs.~accuracy: effect of threshold.{]}
-\item
-  From the above, we select threshold of high accuracy and reasonable
-  cost.
-\item
-  {[}TABLE: Combined system timing vs accuracy: effect of dynamic region
-  selection.{]}
-\end{itemize}
+The R-CNN software was used as available in June 2014\footnote{\url{https://github.com/rbgirshick/rcnn}}.
+That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
+Different images are proposed different numbers of regions.
+\autoref{fig:roi_hist} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
+
+An additional parameter is the size of each batch of regions that goes through the CNN.
+We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
+In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.
+
+\autoref{fig:voc2007_results} and \autoref{tab:results} show the results.
+
+\begin{figure}[ht]
+\centering
+\begin{subfigure}[b]{0.52\linewidth}
+    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
+    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
+\end{subfigure}\hfill
+\begin{subfigure}[b]{0.45\linewidth}
+    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
+    \caption{mAP vs. speed-up factor}\label{fig:speedup}
+\end{subfigure}
+\caption{
+Results on the PASCAL VOC 2007 dataset.
+(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
+For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
+(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
+For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
+}\label{fig:voc2007_results}
+\end{figure}
+
+\begin{table}[ht]
+\centering
+\caption{
+Full table of AP vs. Time results on PASCAL VOC 2007.
+}\label{tab:results}
+\small{
+\include{results_table}
+}
+\end{table}
+
+\begin{description}
+  \item[Original] \hfill \\
+  The original order of the
+  \item[Second] \hfill \\
+  The second item
+  \item[Third] \hfill \\
+  The third etc \ldots
+\end{description}
+
+\begin{figure}
+\centering
+\begin{subfigure}[b]{0.52\linewidth}
+    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
+    \caption{Distribution of number of regions per image.}\label{fig:roi_hist}
+\end{subfigure}\hfill
+\begin{subfigure}[b]{0.46\linewidth}
+    % \includegraphics[width=\linewidth]{PLACEHOLDER}
+    \rule{5cm}{4cm}
+    \caption{\todo{Another small figure here}}\label{fig:PLACEHOLDER}
+\end{subfigure}
+\caption{}
+\end{figure}

### 2014-06-06 method.tex
done with abstract
evaluation figures and some text

@@
 
-Our method builds on the architecture described in \cite{Girshick-CVPR-2014}.
-As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and then does the following: (1) for each ROI, classifies it with a CNN, obtaining multi-class scores; (2) post-processes the scored ROIs with non-maximal suppression and other bounding box refinement to obtain the final detections.
+We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
+As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and for each batch of ROIs, transforms them to canonical size and classifies with a CNN, obtaining multi-class scores.
+After all batches have scores, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
 
-We aim to incorporate several speed-ups into a similar architecture.
-As summarized in \autoref{fig:combined}, we start with the same ROI proposals, and then (1) score each proposal with a quick-to-compute feature; (2) select the ROI that is most promising, and score it with a CNN, which is additionally sped up with a cascaded structure; (3a) either select another ROI, incorporating the scores of the first one into the selection -- or (3b) post-process the ROIs scored so far and exit.
+As summarized in \autoref{fig:combined}, we start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
+We then select a batch of highly-scoring ROIs and classify them with the CNN -- but the CNN may additionally be sped up with cascaded structure.
+After the batch is scored, we optionally re-score the remaining ROIs, and repeat.
 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\linewidth]{figures/roi_hist.pdf}
-\caption{
-    Distribution of the number regions per image on PASCAL VOC2007 validation set.
-}\label{fig:roi_hist}
-\end{figure}
-
-\begin{table}[ht]
-\centering
-\caption{
-Full table of AP vs. Time results on PASCAL VOC 2007.
-}\label{tab:results}
-\include{results_table}
-\end{table}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/_speedup.pdf}
-\caption{
-Speedup.
-}\label{fig:speedup}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.5\linewidth]{figures/_all_selected.pdf}
-\caption{
-AP vs. Time plots.
-}\label{fig:apvst}
-\end{figure}

### 2014-06-06 method.tex
method intro is good and adjusted figure 2

@@
 We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
-As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), and for each batch of ROIs, transforms them to canonical size and classifies with a CNN, obtaining multi-class scores.
-After all batches have scores, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
+As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs).
+ROIs are taken in batches: transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
+After all batches have been scored, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
 
-As summarized in \autoref{fig:combined}, we start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
-We then select a batch of highly-scoring ROIs and classify them with the CNN -- but the CNN may additionally be sped up with cascaded structure.
-After the batch is scored, we optionally re-score the remaining ROIs, and repeat.
+We start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
+We then select a batch of highly-scoring ROIs and classify them with the CNN -- which can additionally be sped up with cascaded structure.
+After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until we're either out of time, or out of regions.
+\autoref{fig:combined} summarizes the process.
 
-For the quick feature, we consider the CNN pixel gradient in \autoref{sec:gradient} and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
+For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions, as described in \autoref{sec:region}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
 The Cascaded CNN is described in \autoref{sec:ccnn}.
-The dynamic region selection is explained in \autoref{sec:dynamic}.
+The region selection is explained in \autoref{sec:dynamic}.
 
@@
 \caption{
-Dynamic region selection combines both speedups and introduces another.
+Our method scores each region of interest with a fast feature (we evaluate several), allowing us to pick promising regions first.
+The regions are classified with the original CNN, or a sped-up Cascade-CNN.
+The properties of the regions can play a role in selecting the next batch of regions.
 }\label{fig:combined}
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Region statistics}\label{sec:region}
 

### 2014-06-06 method.tex
region stats and gradient explanation + figure

@@
 
+We compute a very simple feature for each ROI: its normalized location,
+its scale($\sqrt{\text{width} \times \text{height}}$),
+aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
+and normalized counts of overlapping regions, at different PASCAL overlap \todo{definition} thresholds (0, 0.2, 0.6).
+
+This simple feature works suprisingly well for filtering regions to process first, and is always included in concatenation with the more complex features that are described next.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-    \todo{Explain backprop to pixels.}
-\item
-    \todo{Explain how we featurize it: warp each ROI to canonical size and also include overall statistics, then train to classify $>0.3$ overlap with ground truth.}
-\item
-    \todo{FIGURE: shows schematic structure of the flow and gradient saliency maps for a couple of images.}
-\end{itemize}
+We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
+Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
+Accordingly, we implement a simple multi-label loss layer for this fine-tuning.
+\todo{@sergio: details needed?}
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+To compute the pixel gradient feature, we run this CNN forward from image input to the prediction layer, then backward, all the way to the input pixels.
+\todo{@sergey: waiting on evan for his prior sentences on the subject}
+A couple of example pixel gradient images are shown in \autoref{fig:gradient}.
+
+We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
+For each region to be evaluated, we compute the total gradient sum, sums for each of the corners, and proportions of in-region vs. out-of-region sums.
 
@@
 
-\subsubsection{Design choices}
+% \subsubsection{Design choices}
 
@@
 \begin{table}[ht]
+\centering
 \caption{
@@
 }\label{tab:prcnn}
+\small{
 \input{pyra_rcnn_table}
+}
 \end{table}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  %\todo{Explain design choices (single vs multi scale, finding nearest window, warping.}
-  \todo{Add table}
-\end{itemize}
-
-%\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
 

### 2014-06-06 abstract.tex
shorter abs

--- 2014-06-06 abstract.tex
@@
 \begin{abstract}
-Recently, an object detection architecture with two key points has demonstrated an undeniable increase in performance on the most challenging detection datasets.
-The first point is doing bottom-up Region of Interest (ROI) proposals instead of sliding-window evaluation.
-The second point is using multi-layer Convolutional Neural Nets (CNNs) pre-trained on large-scale classification data to featurize canonically resized ROIs.
-Although state of the art in recognition performance, the method is computationally costly, requiring CNN processing of upwards of two thousand regions.
-Even with efficient GPU implementation, the method takes \textasciitilde 10 s per image after the computation of region proposals.% (another \textasciitilde 2 s).
-
-We propose and evaluate several novel speed-ups for the Region-CNN (R-CNN):
-(1) Initial or ongoing region filtering using one of three ``fast features'': (a) region overlap statistics; (b) CNN pixel gradient statistics; and (c) the \emph{Pyramid R-CNN}, which processes the whole image up to the highest non-fully-connected layer before cropping, resizing, and classifying ROIs.
-(2) \emph{Cascaded CNN}: each ROI passing the initial filter is further processed by a CNN that is augmented with a \emph{reject} option after each layer, allowing much faster but accurate classification.
-
+The recently introduced R-CNN object detection framework has excellent detection accuracy, but is slow, running at 10 seconds per image on a GPU.
+R-CNN is slow because it classifies roughly 2k regions of interest (ROIs) per image without sharing computation between them.
+We propose and evaluate two novel speed-ups for R-CNN:
+(1) Region filtering using one of three ``fast features'': (i) region overlap statistics; (ii) CNN pixel gradient statistics; and (iii) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation;
+and (2) \emph{Cascaded CNN}, which adds a \emph{reject} option after each CNN layer that yields fast but accurate classification.
 We achieve a \textasciitilde 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a \textasciitilde 16x speed-up while losing no more than 20\%.

### 2014-06-06 method.tex
changes
pixel gradient detail

@@
 
-To compute the pixel gradient feature, we run this CNN forward from image input to the prediction layer, then backward, all the way to the input pixels.
-\todo{@sergey: waiting on evan for his prior sentences on the subject}
-A couple of example pixel gradient images are shown in \autoref{fig:gradient}.
+This pixel-wise gradient can be seen as a first-order approximation to the weight of a pixel in the classification output.
+To compute it, we first run the CNN forward from image input to the prediction layer.
+Back-propagating through the model and a last backward pass to the input gives the pixel-wise gradient.
+A couple of example images are shown in \autoref{fig:gradient}.
 
@@
 \caption{
-    Pyramid R-CNN design choices.
+    Pyramid R-CNN design choices, vs mAP performance.
+    We additionally show two best and two worst performing classes.
 }\label{tab:prcnn}

### 2014-06-06 abstract.tex
abs v3

@@
 R-CNN is slow because it classifies roughly 2k regions of interest (ROIs) per image without sharing computation between them.
-We propose and evaluate two novel speed-ups for R-CNN:
-(1) Region filtering using one of three ``fast features'': (i) region overlap statistics; (ii) CNN pixel gradient statistics; and (iii) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation;
-and (2) \emph{Cascaded CNN}, which adds a \emph{reject} option after each CNN layer that yields fast but accurate classification.
-We achieve a \textasciitilde 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a \textasciitilde 16x speed-up while losing no more than 20\%.
+We propose and evaluate two novel speed-ups for R-CNN.
+First, we re-order regions to process the most promising ones first using one of three ``fast features'': (1) region overlap statistics; (2) CNN pixel gradient statistics; and (3) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation.
+Second, we propose a novel \emph{Cascaded CNN} that adds a \emph{reject} option after each CNN layer, which yields fast but accurate classification.
+We achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.
 \end{abstract}

### 2014-06-06 evaluation.tex
region stats and gradient explanation + figure
ergion selection and some more eval setup

@@
   \item[Original] \hfill \\
-  The original order of the
-  \item[Second] \hfill \\
-  The second item
-  \item[Third] \hfill \\
-  The third etc \ldots
+  The original order of the Selective Search regions of interest.
+  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.
+  \item[Random] \hfill \\
+  A completely blind permutation of the original order.
+  \item[Region Selection] \hfill \\
+  The order is determined as described in \autoref{sec:dynamic}.
+  The region statistics feature from \autoref{sec:region} is always used, allowing learning an effective ordering.
+  Additionally, we consider the Pixel Gradient and the Pyramid-R-CNN features.
 \end{description}
@@
 \begin{subfigure}[b]{0.46\linewidth}
-    % \includegraphics[width=\linewidth]{PLACEHOLDER}
-    \rule{5cm}{4cm}
-    \caption{\todo{Another small figure here}}\label{fig:PLACEHOLDER}
+    \includegraphics[width=\linewidth]{figures/gradient.pdf}
+    \caption{Example of the CNN gradient.}\label{fig:gradient}
 \end{subfigure}

### 2014-06-06 method.tex
ergion selection and some more eval setup

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dynamic region selection}\label{sec:dynamic}
+\subsection{Region selection}\label{sec:dynamic}
 
-\autoref{fig:combined} shows the dynamic region selection loop.
+As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
+Unlike the Cascade-CNN, this process of region selection does not reject regions flat out, but merely reorders them to be processed later.
 
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  \todo{Explain dynamic selection of region batches.}
-\item
-  \todo{Explain iterative training procedure.}
-\end{itemize}
+We consider two ways of selecting regions by their score.
+The first is to simply sort the regions by score, and to take batches in that sorted order
+We quickly discovered that this naive method does not result in good performance, and in fact can be worse than taking regions in an entirely random order.
+We hypothesized that this is because the highest scoring regions may all
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
-
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+\subsubsection{Dynamic feature update}

### 2014-06-06 method.tex
sergio's c-cnn section

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Cascaded CNN}\label{sec:ccnn}
@@
 
+To set the thresholds we took a sample of 140K regions from the images in the validation set containing positive and negative examples.
+Then we set the threshold for the rejector after first layer to have 0.8 recall on the positive regions.
+Similarly we set the threshold in for the rejector after the second layer, using the regions that pass the first rejector, to maintain a 0.8 recall on positive regions.
+And finally we set the threshold for the rejector after the third layer, using the regions that pass the first two rejectors, to maintain a 0.8 recall on positive regions.
+After every rejection layer the precision on positive regions increase, going from 0.38 to 0.74, while maintaining a recall of 0.8.
+
+To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:
 \begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  \todo{Explain training the thresholds.}
+\item 1700 ms to process all the layers
+\item 270 ms (15\%) in layer 1 (This includes conv1, relu1, pool1, norm1)
+\item 360 ms (20\%) in layer 2 (This includes conv2, relu2, pool2, norm2)
+\item 285 ms (15\%) in layer 3 (This includes conv3, relu3)
 \end{itemize}
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, layer 3 and those not rejected are  0.15, 0.35, 0.5, 1.0 of the total time taken per region (~1.7 ms).
+
+At test time, I observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch.
+I multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
 

### 2014-06-06 abstract.tex
pivot

@@
 \begin{abstract}
-The recently introduced R-CNN object detection framework has excellent detection accuracy, but is slow, running at 10 seconds per image on a GPU.
-R-CNN is slow because it classifies roughly 2k regions of interest (ROIs) per image without sharing computation between them.
-We propose and evaluate two novel speed-ups for R-CNN.
-First, we re-order regions to process the most promising ones first using one of three ``fast features'': (1) region overlap statistics; (2) CNN pixel gradient statistics; and (3) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation.
-Second, we propose a novel \emph{Cascaded CNN} that adds a \emph{reject} option after each CNN layer, which yields fast but accurate classification.
+We propose a novel cascaded approach for speeding up convolutional neural networks and evaluate it on the recently introduced R-CNN object detection system.
+R-CNN has excellent detection accuracy, but is slow, running at 10 seconds per image on a GPU.
+Most of R-CNN's time is spent classifying roughly 2k regions of interest per image without sharing computation between them.
+Our approach introduces a \emph{reject} option between layers in the CNN, allowing the network to terminate computation early, as in a traditional cascade.
+We also investigate a strong baselines for speeding up R-CNN, including a novel approximation to R-CNN that uses a feature pyramid to amortize region computation.
+These baselines validate the efficacy of the Cascaded CNN.
+%First, we re-order regions to process the most promising ones first using one of three ``fast features'': (1) region overlap statistics; (2) CNN pixel gradient statistics; and (3) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation.
+%Second, we propose a novel \emph{Cascaded CNN} that adds a \emph{reject} option after each CNN layer, which yields fast but accurate classification.
 We achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.

### 2014-06-06 introduction.tex
pivot

--- 2014-05-29 introduction.tex
@@
 
-\todo{
-Standard object detection, deep learning, computational concerns, introduction.
-}
+Multi-layered convolutional models (CNNs) have recently been shown to offer impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
+While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
+OverFeat \cite{Sermanet-ICLR-2014} overcomes this by incrementally computing the CNN features in overlapping windows, but then restricts the window locations to be on a coarse regular grid.
+R-CNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
+While R-CNN has leading performance on PASCAL and ImageNet Detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (not counting region generation).
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+Existing detection schemes, including R-CNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
+They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
+In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
+(Or when time is considered a costly resource.)
+%We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.
 
-\lorem{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+%Our model yields novel forms of ``cascaded''-style processing for such detectors, where large amounts of computation is pruned when it is deemed redundant, or likely unproductive.
+%We consider both static and dynamic policies for such behavior, and features based on low-level cues and mid-level ConvNet features.
+%We focus on speeding up the R-CNN framework, but our work is relevant to any detector that operates a relatively expensive function over a set of candidate locations.
+%Our model implicily learns to look elsewhere when a nearby region is already examined, and to look above a motorbike for a possible person; it generalized well known principles of non-maximal suppression and inter-task context.
+
+%We consider three specific mechanisms, which are independently and jointly valuable.
+%[[ 1) dense eval.; 2) cascade; 3) dynamic ]].
+%Together we call these ``Timely'' methods for object detection, hence the title of our paper.
 

### 2014-06-06 method.tex
done with region selection

@@
 As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
-Unlike the Cascade-CNN, this process of region selection does not reject regions flat out, but merely reorders them to be processed later.
+This process of region selection does not reject regions flat out, but reorders them to be processed later.
 
-We consider two ways of selecting regions by their score.
-The first is to simply sort the regions by score, and to take batches in that sorted order
-We quickly discovered that this naive method does not result in good performance, and in fact can be worse than taking regions in an entirely random order.
-We hypothesized that this is because the highest scoring regions may all
+We first tried to simply sort the regions by score and take batches in that sorted order.
+Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
+We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
 
-\subsubsection{Dynamic feature update}
+Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
+We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.

### 2014-06-06 introduction.tex
intro pivot

@@
 
-Further, unless care is taken in the design of the computation, much of the computation can be repetitive.
-OverFeat \cite{Sermanet-ICLR-2014} overcomes this by incrementally computing the CNN features in overlapping windows, but then restricts the window locations to be on a coarse regular grid.
-R-CNN allows more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows.
-While R-CNN has leading performance on PASCAL and ImageNet Detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (not counting region generation).
+The standard method for quickly applying a CNN to a large number of candidate regions is to restrict the regions to lie in a regular scale-space pyramid.
+With this restriction, the CNN can efficiently compute features for all regions using convolution.
+This approach was used in classical CNN-based detection systems, as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
+The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
+While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (not counting region generation).
 
-Existing detection schemes, including R-CNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
-They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
-In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
-(Or when time is considered a costly resource.)
+In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
+We bring the classical idea of a cascade to CNNs by inserting a \emph{reject} option between layers of the CNN.
+When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
+
+We also consider a variety of strong baselines for speeding up R-CNN.
+One of these baselines is a novel approach that approximates R-CNN by first building a feature pyramid, which is inherently efficient, and then using the pyramid to share features between overlapping region proposals.
+While this methods performs quite well on its own, we show that our Cascaded CNN provides a better speed-up with a simpler approach.
+
+%Existing detection schemes, including R-CNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
+%They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
+%In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
+%(Or when time is considered a costly resource.)
 %We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.

### 2014-06-06 abstract.tex
fix typo

@@
 Our approach introduces a \emph{reject} option between layers in the CNN, allowing the network to terminate computation early, as in a traditional cascade.
-We also investigate a strong baselines for speeding up R-CNN, including a novel approximation to R-CNN that uses a feature pyramid to amortize region computation.
+We also investigate strong baselines for speeding up R-CNN, including a novel approximation to R-CNN that uses a feature pyramid to amortize region computation.
 These baselines validate the efficacy of the Cascaded CNN.

### 2014-06-06 method.tex
Corrected caption and multi-label training

@@
 \section{Method}\label{sec:method}
+
+We consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found, based on inference from relatively lightweight features.
+We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.
+Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.
+We consider approximate measures computed from a grid of mid-level features; this proves to be a powerful signal, and provides a clear boost when the time required to compute that feature is not considered.
+But even with a fast image pyramid to compute them globally for all regions, the time required is unfortunately large enough to significantly dilute their impact.
+
+What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.
+We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other of the methods described above, it can effectively learn a "Timely" approach to the detection computation.
+
+}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
+The Cascaded CNN is described in \autoref{sec:ccnn}.
+The region selection is explained in \autoref{sec:dynamic}.
+
+We first review the base model that our work is derived from, the R-CNN method in the following subsection.
+We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.
+We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.
+Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
+Our region selection method is explained in \autoref{sec:dynamic}.
+
+\subsection{Base model}
 
@@
 \autoref{fig:combined} summarizes the process.
-
-For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions, as described in \autoref{sec:region}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
-The Cascaded CNN is described in \autoref{sec:ccnn}.
-The region selection is explained in \autoref{sec:dynamic}.
 
@@
 \subsection{Region statistics}\label{sec:region}
-
+For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions.
 We compute a very simple feature for each ROI: its normalized location,
@@
 Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
-Accordingly, we implement a simple multi-label loss layer for this fine-tuning.
-\todo{@sergio: details needed?}
+Accordingly, we implement cross-entropy loss layer to train a simple multi-label classifier with binary vector.
 
@@
 \caption{
-The Cascaded CNN has a reject option after pool1, pool2, conv3 and conv4 layers.
+The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
 \todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}

### 2014-06-06 method.tex
tjd

@@
 Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
-Accordingly, we implement cross-entropy loss layer to train a simple multi-label classifier with binary vector.
+Accordingly, we implement a simple multi-label loss layer for this fine-tuning.
+\todo{@sergio: details needed?}
 
@@
 \caption{
-The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
+The Cascaded CNN has a reject option after pool1, pool2, conv3 and conv4 layers.
 \todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}

### 2014-06-06 method.tex
td
done

--- 2014-06-06 method.tex
@@
 We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.
+
 Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.
@@
 
-}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
-The Cascaded CNN is described in \autoref{sec:ccnn}.
-The region selection is explained in \autoref{sec:dynamic}.
-
 We first review the base model that our work is derived from, the R-CNN method in the following subsection.
@@
 Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
-Our region selection method is explained in \autoref{sec:dynamic}.
 
@@
 \autoref{fig:combined} summarizes the process.
+
+As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
+This process of region selection does not reject regions flat out, but reorders them to be processed later.
+
+We first tried to simply sort the regions by score and take batches in that sorted order.
+Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
+We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
+Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
+We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Region selection}\label{sec:dynamic}
-
-As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
-This process of region selection does not reject regions flat out, but reorders them to be processed later.
-
-We first tried to simply sort the regions by score and take batches in that sorted order.
-Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
-We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
-
-Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
-We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
+%\subsection{Region selection}\label{sec:dynamic}

### 2014-06-06 evaluation.tex
evaluation

@@
 
-We evaluate on the standard object detection benchmark: the PASCAL VOC \todo{cite?}.
+We evaluate on the standard object detection benchmark: the PASCAL VOC \cite{pascal-voc-2010}.
 In all cases, the CNN region classifiers are trained on the PASCAL VOC 2007 trainval set.
@@
 
-\autoref{fig:voc2007_results} and \autoref{tab:results} show the results.
+The scoring function for the Region Statistics, Pixel Gradient, and Pyramid R-CNN features is trained by a logistic regression classifier onto the supervised signal of region overlap with ground truth on the validation dataset.
+The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.
+
+The result plots and details are shown in \autoref{fig:voc2007_results} and \autoref{tab:results}.
 
@@
 Full table of AP vs. Time results on PASCAL VOC 2007.
+Best performance for each time point is in bold.
 }\label{tab:results}
@@
 
+\subsubsection{Experiments}
 \begin{description}
@@
   The order is determined as described in \autoref{sec:dynamic}.
-  The region statistics feature from \autoref{sec:region} is always used, allowing learning an effective ordering.
-  Additionally, we consider the Pixel Gradient and the Pyramid-R-CNN features.
+  The region statistics feature from \autoref{sec:region} is always used.
+  Additionally, we consider either the Pixel Gradient and the Pyramid R-CNN features.
+  These two features have a \emph{setup time}: the gradient forward-back propagation takes 20 ms, and the Pyramid R-CNN takes a whopping 800 ms.
+  \item[Cascaded CNN]
+  The Cascaded CNN model, as described in \autoref{sec:ccnn}.
+  The first experiment (C-CNN) takes batches of regions in a random order.
+  The next two experiments also make use of the Region Selection methodology, and the two fast features of Pixel Gradient and the Pyramid R-CNN.
 \end{description}
+
+\subsubsection{Analysis}
+Since the time to process a full batch with a non-cascaded CNN is 500 ms, there are no results for non-cascaded baselines at 300 ms.
+At this time, the Cascaded CNN without any region ordering is best.
+A reason for why C-CNN with Region Selection is not as good at this point is that the region selection presents better region candidates, with fewer rejection opportunities, and thus has less coverage of the image.
+
+At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
+Both method are better than the baseline non-cascaded methods for this entire duration.
+This changes once the Pyramid R-CNN has time to compute and to run through a few batches.
+The later times show best performance from the Region Selection with that feature.
 
@@
 \end{subfigure}\hfill
-\begin{subfigure}[b]{0.46\linewidth}
+\begin{subfigure}[b]{0.33\linewidth}
     \includegraphics[width=\linewidth]{figures/gradient.pdf}

### 2014-06-06 evaluation.tex
remove todos

@@
 
-\subsubsection{Experiments}
+\subsection{Experiments}
 \begin{description}
@@
   \item[Region Selection] \hfill \\
-  The order is determined as described in \autoref{sec:dynamic}.
   The region statistics feature from \autoref{sec:region} is always used.
@@
 
-\subsubsection{Analysis}
+\subsection{Analysis}
 Since the time to process a full batch with a non-cascaded CNN is 500 ms, there are no results for non-cascaded baselines at 300 ms.

### 2014-06-06 method.tex
remove todos

@@
 aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
-and normalized counts of overlapping regions, at different PASCAL overlap \todo{definition} thresholds (0, 0.2, 0.6).
+and normalized counts of overlapping regions, at different PASCAL overlap thresholds (0, 0.2, 0.6).
 
@@
 The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
-\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
 }\label{fig:ccnn}

### 2014-06-06 conclusion.tex
concl

--- 2014-05-29 conclusion.tex
@@
-\section{Conclusion}\label{conclusion}
+%!TEX root=paper.tex
+\section{Conclusion}\label{sec:conclusion}
 
-{[}Standard stuff{]}
-
-\subsection{Future work}\label{future-work}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  ?
-\end{itemize}
+We have presented approaches to speed up region-based convolutional
+object detectors. Our approach is based on the reprioritization of
+candidate regions so as to maximize mAP within a given time budget.
+We consider techniques based on both re-ranking and
+rejection-filtering based on lightweight features of the observed
+image region.  We re-order regions to process the most promising ones
+first using one of three ``fast features'' based on region overlap
+statistics, CNN pixel gradient statistics, and a convnet feature
+pyramid.  While our work is generally applicable to any windowed
+detection, we specifically develop a novel cascaded approach for
+speeding up convolutional neural networks and evaluate it on the
+recently introduced R-CNN object detection system, which has excellent
+detection accuracy but is realtively slow. We show how to effecively
+amortize the time R-CNN spends classifying regions of interest by
+sharing computation between overlapping regions, and pruning regions
+unlikely to be valuable.  Our approach introduces a \emph{reject}
+option between layers in the CNN, allowing the network to terminate
+computation early, as in a traditional cascade.  We reported
+significant speed-ups while losing a modest amount of detection
+performance. Our scheme allows R-CNN to be used in time-critical
+applications.

### 2014-06-06 method.tex
typos

@@
 What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.
-We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other of the methods described above, it can effectively learn a "Timely" approach to the detection computation.
+We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a "Timely" approach to the detection computation.
 
-We first review the base model that our work is derived from, the R-CNN method in the following subsection.
+We first review the base model that our work is derived from, the R-CNN method, in the following subsection.
 We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.
 We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.
-Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
+Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or expoit more costly mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
 

### 2014-06-06 method.tex
minor changes

@@
 What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.
-We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a "Timely" approach to the detection computation.
+We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a ``Timely'' approach to the detection computation.
 
@@
 We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
-Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
-We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
+Guided by this intuition, we consider a more dynamic approach to region selection:
+we put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
 
@@
 Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
-Accordingly, we implement cross-entropy loss layer to train a simple multi-label classifier with binary vector.
+Accordingly, we implement a cross-entropy loss layer to train a simple multi-label classifier with binary vector.
 
@@
 It would be useful to quickly reject these regions, without expending the full amount of computation on them.
-Since most of the time is spend in the convolution layers, we introduce a reject layer after pool1, pool2, conv3 and conv4, this allows skipping the computation of the following convolutions.
+Since most of the time is spend in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
 These reject layers were trained using the corresponding fine-tuned CNN.
@@
 To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:
+
 \begin{itemize}
 \item 1700 ms to process all the layers
-\item 270 ms (15\%) in layer 1 (This includes conv1, relu1, pool1, norm1)
-\item 360 ms (20\%) in layer 2 (This includes conv2, relu2, pool2, norm2)
-\item 285 ms (15\%) in layer 3 (This includes conv3, relu3)
+\item 270 ms (15\%) in layer 1 (This includes \texttt{conv1}, \texttt{relu1}, \texttt{pool1}, \texttt{norm1})
+\item 360 ms (20\%) in layer 2 (This includes \texttt{conv2}, \texttt{relu2}, \texttt{pool2}, \texttt{norm2})
+\item 285 ms (15\%) in layer 3 (This includes \texttt{conv3}, \texttt{relu3})
 \end{itemize}
@@
 
-At test time, I observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch.
-I multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
+At test time, we observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch.
+We multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
 
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Region selection}\label{sec:dynamic}

### 2014-06-06 related_work.tex
minor changes

@@
 \paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}
-The recent success of deep convolutional neural networks (CNN) Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has spurred various investigations \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} how this success can be carried over to an detection task despite the prohibitive cost of evaluating such models densely in a naive manner.
-These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014} as well as deriving a window sampling scheme that is based on the gradient of the network \cite{Simonyan-ICLR-2014}.
-All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
-In contrast to previous work on shared dense computation layers in CNN classifiers for detection \cite{Sermanet-ICLR-2014}, we maintain effective canonicalization of regions and show its importance for achieving high performance.
+
+The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} .
+
+These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.
+All these method have a fixed strategy and are unable to adapt their computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
 
@@
 \paragraph{Dynamic selection}\label{dynamic-selection}
-Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}.
-We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware.
-In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.
+Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,dulac2014}.
+In particular, we combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.

### 2014-06-06 method.tex
typo

--- 2014-06-06 method.tex
@@
 It would be useful to quickly reject these regions, without expending the full amount of computation on them.
-Since most of the time is spend in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
+Since most of the time is spent in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
 These reject layers were trained using the corresponding fine-tuned CNN.

### 2014-06-06 method.tex
layers on layers on layers

@@
 It would be useful to quickly reject these regions, without expending the full amount of computation on them.
-Since most of the time is spent in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
+Since most of the time is spent in the convolutional layers, we introduce a reject option after \texttt{pool1}, \texttt{pool2}, and \texttt{conv3}, this allows skipping the computation of the following convolutions.
 These reject layers were trained using the corresponding fine-tuned CNN.

### 2014-06-06 introduction.tex
8 pages

@@
 
-Multi-layered convolutional models (CNNs) have recently been shown to offer impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
+Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
 While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.
@@
 In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
-We bring the classical idea of a cascade to CNNs by inserting a \emph{reject} option between layers of the CNN.
+We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
 When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.

### 2014-06-06 evaluation.tex
minor changes
8 pages
Final touches

@@
 Different images are proposed different numbers of regions.
-\autoref{fig:roi_hist} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
-
+\autoref{fig:roi_hist_and_gradient} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
 An additional parameter is the size of each batch of regions that goes through the CNN.
@@
   These two features have a \emph{setup time}: the gradient forward-back propagation takes 20 ms, and the Pyramid R-CNN takes a whopping 800 ms.
-  \item[Cascaded CNN]
+  \item[Cascaded CNN] \hfill \\
   The Cascaded CNN model, as described in \autoref{sec:ccnn}.
@@
 \centering
-\begin{subfigure}[b]{0.52\linewidth}
-    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
-    \caption{Distribution of number of regions per image.}\label{fig:roi_hist}
-\end{subfigure}\hfill
-\begin{subfigure}[b]{0.33\linewidth}
-    \includegraphics[width=\linewidth]{figures/gradient.pdf}
-    \caption{Example of the CNN gradient.}\label{fig:gradient}
-\end{subfigure}
-\caption{}
+\includegraphics[width=0.52\linewidth]{figures/roi_hist.pdf}
+\hfill
+\includegraphics[width=0.4\linewidth]{figures/gradient.pdf}
+\caption{
+(left) Distribution of number of regions per image.
+(right) Example of the CNN gradient.
+}\label{fig:roi_hist_and_gradient}
 \end{figure}

### 2014-08-10 nips_rebuttal_1262.txt
nips reviews and rebuttals

Summaries (scores)
------------------
Assigned_Reviewer_15 (5): This paper is an extension of the R-CNN window proposal-based object detection algorithm of Girshick et al.'CVPR 2014. The novelty of the paper is limited but it has an interesting idea of using the output of the intermediate layers in the CNN hierarchy. The experiments are solid and demonstrate speeding-up R-CNN, at only a reasonable loss in performance. However, most of the speedup can be obtained by training a foreground-background classifier on the window proposals and processing the highest-scoring ones. The paper lacks details at multiple places needed to reproduce the results. The significance beyond the specific set-up of Girshick et al.'14 is not clear.

Assigned_Reviewer_43 (4): This paper presents several approaches to speed up the Region-based CNN. The approaches are rather heuristic and the novelty is limited. The experimental evaluations are not adequate either.

Assigned_Reviewer_9 (7): Speeding up the very slow but state-of-the-art R-CNN algorithm is of practical consequence for computer vision and the current paper offers a comprehensive and well-performing solution using a collection of suitable approaches. The paper is generally well written and experimental results are convincing.

Rebuttal
--------
We thank the reviewers for their thoughtful consideration.
We feel that the reviewers underestimated the impact of the Cascaded CNN we report, and see the need for a more clear rhetorical focus on this contribution.

Addressing specific concerns:

- "For the "Pixel gradient" method. What is the gradient computed here? Gradient with respect to the loss? What is the loss used (does it allow multiple labels per image)? Is the network applied to the whole image? How does the method deal with non-square images?"

Our method follows reference [7] (http://arxiv.org/abs/1312.6034) to the best of our knowledge. Images are resized to square and classified with an "AlexNet" CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss. At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.

- "For the "Cascade" method. What form of the classifier is used here? Are the feature maps processed in any way before training the classifier?"

Each cascade classifier is implemented as a fully-connected layer following a linear rectification, trained with simple logistic loss using foreground/background labels (and with dropout).

- "Will the rejected regions in the cascaded CNN be re-processed? If not, its performance should be worse than the original R-CNN at the 10000 ms time allotted (see Table. 2), as the true-positives might be filtered out in the early stage."

The answer is yes, and the reviewer is correct about the implications. This is our mistake: the table entries for C-CNN methods at 10,000 ms should be blank.

- "How will the performance change if using the different batch size?"

This is an empirical question and thus a great experimental suggestion that we will execute.

- "The paper does not explain why removing certain regions using the cascaded approach can be done efficiently in the batch, on GPU. Do we lose some efficiency from not applying batch-optimized routines?"

In the very efficient implementation of CNNs we use (Caffe), there is a simple loop over each batch element in both CPU and GPU convolution code. We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade. It's true that the memory remains needlessly occupied, but we do consider this a problem with our large-capacity GPUs.

- "If each region rejection layer is tuned to have 80% recall on positive regions, wouldn't the combination of all of them end up with less than 80% recall? Also, 80% positive recall at each stage seems too low?"

This is correct, and is an empirical question that we are running additional experiments to answer.

- "Perhaps another way of prioritizing regions by quick-to-compute score is to pick batches of regions with high scores that don't overlap too much (using non-max-suppression estimates to diversify the region set)? This is a potential alternative to the current scheme, unclear if it would help."

This is a scheme we considered but decided against, due to the additional time required to run non-maximum suppression. Also keep in mind that our region proposal mechanism does not provide confidences to regions, making non-maximum suppression only slightly more meaningful than our current random scheme.

### 2014-08-11 nips_rebuttal_1262.txt
fixes to rebuttal

@@
 
-The answer is yes, and the reviewer is correct about the implications. This is our mistake: the table entries for C-CNN methods at 10,000 ms should be blank.
+The answer is no, they will not be re-processed, and the reviewer is correct about the implications. This is our mistake: the table entries for C-CNN methods at 10,000 ms should be blank.
 
@@
 We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade.
-It's true that the memory remains needlessly occupied, but we do consider this a problem with our large-capacity GPUs.
+It's true that the memory remains needlessly occupied, but we do not consider this a problem with large-capacity GPUs.
 
@@
 
-This is correct, and is an empirical question that we are running additional experiments to answer.
+This is correct, with a caveat: the thresholds are trained on a dataset of equal proportion positive/negative examples, while the actual dataset has much more negative than positive examples.
+Regardless, this is an empirical question that we are running additional experiments to answer.
 

### 2014-08-11 ccnn_fig.tex
removing everything about p-rcnn; restructuring method section

--- 2014-06-06 method.tex
@@
-%!TEX root=paper.tex
-\section{Method}\label{sec:method}
-
-We consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found, based on inference from relatively lightweight features.
-We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.
-
-Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.
-We consider approximate measures computed from a grid of mid-level features; this proves to be a powerful signal, and provides a clear boost when the time required to compute that feature is not considered.
-But even with a fast image pyramid to compute them globally for all regions, the time required is unfortunately large enough to significantly dilute their impact.
-
-What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.
-We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a "Timely" approach to the detection computation.
-
-We first review the base model that our work is derived from, the R-CNN method, in the following subsection.
-We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.
-We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.
-Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or expoit more costly mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
-
-\subsection{Base model}
-
-We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
-As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs).
-ROIs are taken in batches: transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
-After all batches have been scored, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
-
-We start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
-We then select a batch of highly-scoring ROIs and classify them with the CNN -- which can additionally be sped up with cascaded structure.
-After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until we're either out of time, or out of regions.
-\autoref{fig:combined} summarizes the process.
-
-As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
-This process of region selection does not reject regions flat out, but reorders them to be processed later.
-
-We first tried to simply sort the regions by score and take batches in that sorted order.
-Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
-We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
-Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
-We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
-\caption{
-R-CNN architecture: image regions are cropped, resized, and each one fed through a CNN with classification layers.
-The classifier outputs are post-processed to give the final detections.
-}\label{fig:rcnn}
-\end{center}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
-\caption{
-Our method scores each region of interest with a fast feature (we evaluate several), allowing us to pick promising regions first.
-The regions are classified with the original CNN, or a sped-up Cascade-CNN.
-The properties of the regions can play a role in selecting the next batch of regions.
-}\label{fig:combined}
-\end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Region statistics}\label{sec:region}
-For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions.
-We compute a very simple feature for each ROI: its normalized location,
-its scale($\sqrt{\text{width} \times \text{height}}$),
-aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
-and normalized counts of overlapping regions, at different PASCAL overlap thresholds (0, 0.2, 0.6).
-
-This simple feature works suprisingly well for filtering regions to process first, and is always included in concatenation with the more complex features that are described next.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CNN pixel gradient computation}\label{sec:gradient}
-
-One fast-to-compute feature we consider for the preliminary featurization of ROIs is the pixel gradient, back-propagated throgh the classifier CNN applied to the whole image.
-This gradient corresponds to a kind of saliency map onto the image \cite{Simonyan-ICLR-2014}, and can therefore be used to evaluate ROIs.
-
-We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
-Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
-Accordingly, we implement a cross-entropy loss layer to train a simple multi-label classifier with binary vector.
-
-This pixel-wise gradient can be seen as a first-order approximation to the weight of a pixel in the classification output.
-To compute it, we first run the CNN forward from image input to the prediction layer.
-Back-propagating through the model and a last backward pass to the input gives the pixel-wise gradient.
-A couple of example images are shown in \autoref{fig:gradient}.
-
-We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
-For each region to be evaluated, we compute the total gradient sum, sums for each of the corners, and proportions of in-region vs. out-of-region sums.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pyramid amortized R-CNN}\label{sec:dense}
-
-Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
-We call this multiscale CNN output a ``feature pyramid''.
-As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the feature pyramid at the best matching scale, warped to a canonical size, and classified.
-ROIs are highly overlapping, but their featurization is shared through the pyramid, amortizing its construction cost.
-This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.
-
-% \subsubsection{Design choices}
-
-We explored a variety of choices while designing Pyramid R-CNN.
-We tried using a single scale or a pyramid with 7 levels each separated by a scale factor of $2^{-1/2}$.
-For warping, we experimented with canonical sizes of $s \times s$, for $s \in \{5,6,7\}$ and resampling with nearest neighbor or bilinear interpolation.
-We also tried two variants of the feature pyramid: the raw feature pyramid or one where each level is max pooled with a $3 \times 3$ pooling window run at a stride of $1$ (to avoid subsampling).
-
-\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
-The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
-The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
-The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
-Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.
-
-To map a ROI $R$ into the pyramid, we start by computing an ``optimal'' scale defined by $\alpha^* = 227/\min(h,w)$, where $h$ and $w$ are image height and width of $R$.
-We then find the nearest level in the pyramid: $l^* = \textrm{argmin}_l |\log(\alpha_l) - \log(\alpha^*)|$, where $\alpha_l$ is the scale factor for pyramid level $l$.
-This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.
-
-\begin{table}[ht]
-\centering
-\caption{
-    Pyramid R-CNN design choices, vs mAP performance.
-    We additionally show two best and two worst performing classes.
-}\label{tab:prcnn}
-\small{
-\input{pyra_rcnn_table}
-}
-\end{table}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
-\caption{
-Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
-Regions are cropped from that layer at the best matching scale, resized, and classified.
-}\label{fig:dense_rcnn}
-\end{center}
-\end{figure}
-
-\subsection{Cascaded CNN}\label{sec:ccnn}
-
-Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
-It would be useful to quickly reject these regions, without expending the full amount of computation on them.
-Since most of the time is spend in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
-These reject layers were trained using the corresponding fine-tuned CNN.
-
-The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to reject the region since it is background.
-For our purpose, the reject layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
-The last classification layer still outputs the full multi-class scores for the surviving regions.
-
-To set the thresholds we took a sample of 140K regions from the images in the validation set containing positive and negative examples.
-Then we set the threshold for the rejector after first layer to have 0.8 recall on the positive regions.
-Similarly we set the threshold in for the rejector after the second layer, using the regions that pass the first rejector, to maintain a 0.8 recall on positive regions.
-And finally we set the threshold for the rejector after the third layer, using the regions that pass the first two rejectors, to maintain a 0.8 recall on positive regions.
-After every rejection layer the precision on positive regions increase, going from 0.38 to 0.74, while maintaining a recall of 0.8.
-
-To estimate the saving on time by using the rejectors we timed the time spend to process 1000 regions (10 batches or 100) and the time expended in each of the first 3 layers:
-\begin{itemize}
-\item 1700 ms to process all the layers
-\item 270 ms (15\%) in layer 1 (This includes conv1, relu1, pool1, norm1)
-\item 360 ms (20\%) in layer 2 (This includes conv2, relu2, pool2, norm2)
-\item 285 ms (15\%) in layer 3 (This includes conv3, relu3)
-\end{itemize}
-
-Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, layer 3 and those not rejected are  0.15, 0.35, 0.5, 1.0 of the total time taken per region (~1.7 ms).
-
-At test time, we observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch.
-We multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
-
 \begin{figure}[h!]

### 2014-08-11 evaluation.tex
removing everything about p-rcnn; restructuring method section

@@
 
-The R-CNN software was used as available in June 2014\footnote{\url{https://github.com/rbgirshick/rcnn}}.
+The scoring function for the quick-to-compute features is trained by a logistic regression classifier onto the max PASCAL overlap with any ground truth window on the validation dataset.
+The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.
+
+The R-CNN software was used as available in June 2014.
+\footnote{\url{https://github.com/rbgirshick/rcnn}}
 That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
@@
 
-The scoring function for the Region Statistics, Pixel Gradient, and Pyramid R-CNN features is trained by a logistic regression classifier onto the supervised signal of region overlap with ground truth on the validation dataset.
-The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.
-
 The result plots and details are shown in \autoref{fig:voc2007_results} and \autoref{tab:results}.
 
-\begin{figure}[ht]
-\centering
-\begin{subfigure}[b]{0.52\linewidth}
-    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
-    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
-\end{subfigure}\hfill
-\begin{subfigure}[b]{0.45\linewidth}
-    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
-    \caption{mAP vs. speed-up factor}\label{fig:speedup}
-\end{subfigure}
-\caption{
-Results on the PASCAL VOC 2007 dataset.
-(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
-For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
-(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
-For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
-}\label{fig:voc2007_results}
-\end{figure}
+\input{voc2007_fig}
 
-\begin{table}[ht]
-\centering
-\caption{
-Full table of AP vs. Time results on PASCAL VOC 2007.
-Best performance for each time point is in bold.
-}\label{tab:results}
-\small{
-\include{results_table}
-}
-\end{table}
+\input{voc2007_table}
 
@@
   This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.
+
   \item[Random] \hfill \\
   A completely blind permutation of the original order.
+
   \item[Region Selection] \hfill \\
   The region statistics feature from \autoref{sec:region} is always used.
-  Additionally, we consider either the Pixel Gradient and the Pyramid R-CNN features.
-  These two features have a \emph{setup time}: the gradient forward-back propagation takes 20 ms, and the Pyramid R-CNN takes a whopping 800 ms.
+  Additionally, we consider the Pixel Gradient feature, with \emph{setup time} of the gradient forward-back propagation of 20 ms.
+
   \item[Cascaded CNN] \hfill \\
@@
   The first experiment (C-CNN) takes batches of regions in a random order.
-  The next two experiments also make use of the Region Selection methodology, and the two fast features of Pixel Gradient and the Pyramid R-CNN.
+  The next two experiments also make use of the Region Selection methodology with the quick-to-compute feature.
 \end{description}
@@
 Both method are better than the baseline non-cascaded methods for this entire duration.
-This changes once the Pyramid R-CNN has time to compute and to run through a few batches.
-The later times show best performance from the Region Selection with that feature.
 

### 2014-08-11 introduction.tex
removing everything about p-rcnn; restructuring method section

@@
 
-Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object recognition tasks to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
-While convolutional models are inherently efficient to implement, as convolution itself is a parallelizable and long studied computational primitive, the amount of work to perform complete inference at all candidate region windows is considerable.
+Multi-layered convolutional models (CNNs) have recently demonstrated impressive levels of performance on visual detection tasks, by applying deep CNNs trained on object classification data to multiple candidate image windows in a scene \cite{Sermanet-ICLR-2014,Girshick-CVPR-2014}.
+While convolutional models are efficient to implement due to the availability of high-performance primitives, the amount of work to perform complete inference at all candidate region windows is still considerable.
 
@@
 With this restriction, the CNN can efficiently compute features for all regions using convolution.
-This approach was used in classical CNN-based detection systems, as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
+This approach was used in classical CNN-based detection systems as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
 The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
-While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (not counting region generation).
+While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (following a separate region generation step).
 
-In this paper, we investigate a novel approach for speeding up R-CNN by proposing a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection).
+In this paper, we investigate a novel approach for speeding up R-CNN and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
 We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
 When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
-
 We also consider a variety of strong baselines for speeding up R-CNN.
-One of these baselines is a novel approach that approximates R-CNN by first building a feature pyramid, which is inherently efficient, and then using the pyramid to share features between overlapping region proposals.
-While this methods performs quite well on its own, we show that our Cascaded CNN provides a better speed-up with a simpler approach.
-
-%Existing detection schemes, including R-CNN and OverFeat, are generally relatively naive in terms of the temporal properties of their inference.
-%They take all regions as equal when performing search, and in contrast to human performance, do not consider any attentive or time-sequential aspects.
-%In this paper we advocate for such a perspective, and formulate ``Timely'' detectors which explicitly optimize over the order of regions to consider to maximize their efficacy over time.
-%(Or when time is considered a costly resource.)
-%We build on the work of \cite{Karayev-NIPS-2012}, who considered time-sensitive feature selection in a classification paradigm, but extend the model to be relevant to contemporary detector settings, and to include spatial reasoning.
-
-%Our model yields novel forms of ``cascaded''-style processing for such detectors, where large amounts of computation is pruned when it is deemed redundant, or likely unproductive.
-%We consider both static and dynamic policies for such behavior, and features based on low-level cues and mid-level ConvNet features.
-%We focus on speeding up the R-CNN framework, but our work is relevant to any detector that operates a relatively expensive function over a set of candidate locations.
-%Our model implicily learns to look elsewhere when a nearby region is already examined, and to look above a motorbike for a possible person; it generalized well known principles of non-maximal suppression and inter-task context.
-
-%We consider three specific mechanisms, which are independently and jointly valuable.
-%[[ 1) dense eval.; 2) cascade; 3) dynamic ]].
-%Together we call these ``Timely'' methods for object detection, hence the title of our paper.
-
-We discuss related work in \autoref{sec:related}, cover all parts of our proposed method in \autoref{sec:method}, and present evaluation results on the PASCAL VOC in \autoref{sec:evaluation}.

### 2014-08-11 method.tex
Final touches
removing everything about p-rcnn; restructuring method section

--- 2014-06-06 method.tex
@@
 
-We consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found, based on inference from relatively lightweight features.
-We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.
+We first consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
+We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.
 
-Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.
-We consider approximate measures computed from a grid of mid-level features; this proves to be a powerful signal, and provides a clear boost when the time required to compute that feature is not considered.
-But even with a fast image pyramid to compute them globally for all regions, the time required is unfortunately large enough to significantly dilute their impact.
+We take the R-CNN \cite{Girshick-CVPR-2014} method as our point of departure.
+As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs), which are transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
+After all batches of ROIs have been scored, they are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
 
-What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.
-We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other methods below, it can effectively learn a ``Timely'' approach to the detection computation.
+As summarized in \autoref{fig:combined}, we begin with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
+We then select a batch of highly-scoring ROIs and classify them with the CNN -- which is additionally sped up with cascaded structure.
+After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until either time or regions are depleted.
 
-We first review the base model that our work is derived from, the R-CNN method, in the following subsection.
-We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.
-We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.
-Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or expoit more costly mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time.
-
-\subsection{Base model}
-
-We take the Region-CNN (R-CNN) \cite{Girshick-CVPR-2014} method as our point of departure.
-As summarized in \autoref{fig:rcnn}, R-CNN starts with external region-of-interest proposals (ROIs).
-ROIs are taken in batches: transformed to canonical size, and classified with a CNN, obtaining multi-class scores for each region.
-After all batches have been scored, ROIs are post-processed with non-maximal suppression and other bounding box refinement to obtain the final detections.
-
-We start with the same ROI proposals, but first score all proposals with a quick-to-compute feature.
-We then select a batch of highly-scoring ROIs and classify them with the CNN -- which can additionally be sped up with cascaded structure.
-After the batch is scored, we optionally re-score the remaining ROIs, and repeat the process until we're either out of time, or out of regions.
-\autoref{fig:combined} summarizes the process.
-
-As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
+The quick-to-compute feature is used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
 This process of region selection does not reject regions flat out, but reorders them to be processed later.
 
-We first tried to simply sort the regions by score and take batches in that sorted order.
-Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
-We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
-Guided by this intuition, we consider a more dynamic approach to region selection:
-we put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
+We found that simply sorting the regions by score and taking batches in that sorted order results in poor performance, and can be worse than taking regions in an entirely random order, as the highest scoring regions may be highly overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.
+Instead, we put regions in random order, set a threshold for the quick-to-compute feature such that only half of the unprocessed regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/rcnn.pdf}
-\caption{
-R-CNN architecture: image regions are cropped, resized, and each one fed through a CNN with classification layers.
-The classifier outputs are post-processed to give the final detections.
-}\label{fig:rcnn}
-\end{center}
-\end{figure}
+\input{rcnn_fig}
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/combined.pdf}
-\caption{
-Our method scores each region of interest with a fast feature (we evaluate several), allowing us to pick promising regions first.
-The regions are classified with the original CNN, or a sped-up Cascade-CNN.
-The properties of the regions can play a role in selecting the next batch of regions.
-}\label{fig:combined}
-\end{center}
-\end{figure}
+\input{combined_fig}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Region statistics}\label{sec:region}
-For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions.
-We compute a very simple feature for each ROI: its normalized location,
-its scale($\sqrt{\text{width} \times \text{height}}$),
-aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
-and normalized counts of overlapping regions, at different PASCAL overlap thresholds (0, 0.2, 0.6).
+\subsection{Quick-to-compute feature}
 
-This simple feature works suprisingly well for filtering regions to process first, and is always included in concatenation with the more complex features that are described next.
+\paragraph{Region statistics}\label{sec:region}
+For the first source of information, we consider statistics about ROI location and overlap with other regions.
+For each ROI, we compute: its normalized location, its scale($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CNN pixel gradient computation}\label{sec:gradient}
+This simple feature works suprisingly well for filtering regions to process first.
+In concatenation, we also consider the \emph{pixel gradient}, back-propagated throgh a classification CNN applied to the whole image.
+This feature corresponds to a kind of saliency map, giving an estimate of the importance of each pixel to the final classification of the image.
 
-One fast-to-compute feature we consider for the preliminary featurization of ROIs is the pixel gradient, back-propagated throgh the classifier CNN applied to the whole image.
-This gradient corresponds to a kind of saliency map onto the image \cite{Simonyan-ICLR-2014}, and can therefore be used to evaluate ROIs.
-
-We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
-Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
-Accordingly, we implement a cross-entropy loss layer to train a simple multi-label classifier with binary vector.
-
-This pixel-wise gradient can be seen as a first-order approximation to the weight of a pixel in the classification output.
-To compute it, we first run the CNN forward from image input to the prediction layer.
-Back-propagating through the model and a last backward pass to the input gives the pixel-wise gradient.
-A couple of example images are shown in \autoref{fig:gradient}.
+Our method follows \cite{Simonyan-ICLR-2014} to the best of our knowledge.
+Images are resized to square and classified with an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss.
+(Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.)
+At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.
+A couple of example images are shown in \autoref{fig:roi_hist_and_gradient}.
 
 We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
-For each region to be evaluated, we compute the total gradient sum, sums for each of the corners, and proportions of in-region vs. out-of-region sums.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Pyramid amortized R-CNN}\label{sec:dense}
-
-Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
-We call this multiscale CNN output a ``feature pyramid''.
-As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the feature pyramid at the best matching scale, warped to a canonical size, and classified.
-ROIs are highly overlapping, but their featurization is shared through the pyramid, amortizing its construction cost.
-This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.
-
-% \subsubsection{Design choices}
-
-We explored a variety of choices while designing Pyramid R-CNN.
-We tried using a single scale or a pyramid with 7 levels each separated by a scale factor of $2^{-1/2}$.
-For warping, we experimented with canonical sizes of $s \times s$, for $s \in \{5,6,7\}$ and resampling with nearest neighbor or bilinear interpolation.
-We also tried two variants of the feature pyramid: the raw feature pyramid or one where each level is max pooled with a $3 \times 3$ pooling window run at a stride of $1$ (to avoid subsampling).
-
-\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
-The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
-The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
-The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
-Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.
-
-To map a ROI $R$ into the pyramid, we start by computing an ``optimal'' scale defined by $\alpha^* = 227/\min(h,w)$, where $h$ and $w$ are image height and width of $R$.
-We then find the nearest level in the pyramid: $l^* = \textrm{argmin}_l |\log(\alpha_l) - \log(\alpha^*)|$, where $\alpha_l$ is the scale factor for pyramid level $l$.
-This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.
-
-\begin{table}[ht]
-\centering
-\caption{
-    Pyramid R-CNN design choices, vs mAP performance.
-    We additionally show two best and two worst performing classes.
-}\label{tab:prcnn}
-\small{
-\input{pyra_rcnn_table}
-}
-\end{table}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
-\caption{
-Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
-Regions are cropped from that layer at the best matching scale, resized, and classified.
-}\label{fig:dense_rcnn}
-\end{center}
-\end{figure}
+For each region to be evaluated, we compute the image-normalized gradient sum, sums for each of four corners, and ratio of in-region vs. out-of-region sums.
 
@@
 
-Most ROIs that go through the CNN in R-CNN do not contain objects of interest, and are simply background.
+Most ROIs that are scored in R-CNN do not contain any object of interest.
 It would be useful to quickly reject these regions, without expending the full amount of computation on them.
-Since most of the time is spent in the convolution layers, we introduce a reject layer after layer 1, 2, and 3, this allows skipping the computation of the following convolutions.
-These reject layers were trained using the corresponding fine-tuned CNN.
 
-The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep computing the input with the next layer, or to reject the region since it is background.
-For our purpose, the reject layers are trained to separate Background/Foreground, terminating if they are confident that the input is Background.
+The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
+Each reject layer is implemented as a fully-connected layer following a linear rectification, trained with dropout using logistic loss on foreground/background labels.
+We set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.
+
+In the efficient implementation of CNNs we use (Caffe), there is a simple loop over each batch element in both CPU and GPU convolution code.
+We modify this loop to simply not perform convolution on those elements that were rejected earlier in the cascade.
+\footnote{While memory remains occupied in this scheme, we do not consider this a problem.}
+
+Since most of the time is spent in the convolutional layers, we introduce a reject option after \texttt{pool1}, \texttt{pool2}, and \texttt{conv3}.
 The last classification layer still outputs the full multi-class scores for the surviving regions.
-
-To set the thresholds we took a sample of 140K regions from the images in the validation set containing positive and negative examples.
-Then we set the threshold for the rejector after first layer to have 0.8 recall on the positive regions.
-Similarly we set the threshold in for the rejector after the second layer, using the regions that pass the first rejector, to maintain a 0.8 recall on positive regions.
-And finally we set the threshold for the rejector after the third layer, using the regions that pass the first two rejectors, to maintain a 0.8 recall on positive regions.
-After every rejection layer the precision on positive regions increase, going from 0.38 to 0.74, while maintaining a recall of 0.8.
 
@@
 
-Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, layer 3 and those not rejected are  0.15, 0.35, 0.5, 1.0 of the total time taken per region (~1.7 ms).
+Therefore the expected ``lifetimes'' of regions rejected after layer 1, layer 2, and layer 3 are  0.15, 0.35, and 0.5 of the total time taken per region.
 
-At test time, we observe how many regions out of the batch size of 100 survive each round of thresholding, and then have a weighted average of a region lifetime in that batch.
-We multiply the standard batch time of 500ms by that average region lifetime to arrive at the batch time of the cascaded CNN.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
-\caption{
-The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
-}\label{fig:ccnn}
-\end{center}
-\end{figure}
+\input{ccnn_fig}

### 2014-08-11 pyramid_rcnn.tex
removing everything about p-rcnn; restructuring method section

% This text is abandoned but kept here for archiving.

\subsection{Pyramid amortized R-CNN}\label{sec:dense}

Another fast ROI featurization we consider is a variant of R-CNN that processes the whole image, at multiple scales, with the CNN up to the topmost non-fully-connected layer.
We call this multiscale CNN output a ``feature pyramid''.
As \autoref{fig:dense_rcnn} shows, ROIs are then cropped from the feature pyramid at the best matching scale, warped to a canonical size, and classified.
ROIs are highly overlapping, but their featurization is shared through the pyramid, amortizing its construction cost.
This doesn't work as well as the original R-CNN system, but is much faster, and can therefore be used as the fast feature for the dynamic region selection.

% \subsubsection{Design choices}

We explored a variety of choices while designing Pyramid R-CNN.
We tried using a single scale or a pyramid with 7 levels each separated by a scale factor of $2^{-1/2}$.
For warping, we experimented with canonical sizes of $s \times s$, for $s \in \{5,6,7\}$ and resampling with nearest neighbor or bilinear interpolation.
We also tried two variants of the feature pyramid: the raw feature pyramid or one where each level is max pooled with a $3 \times 3$ pooling window run at a stride of $1$ (to avoid subsampling).

\autoref{tab:prcnn} shows mAP performance on PASCAL VOC 2007 test for these various choices.
The best configuration, in terms of mAP, uses a 7 level pyramid, a warp size of $7 \times 7$ with bilinear interpolation, and max pooling.
The first level of our pyramid is computed from a $1713 \times 1713$ pixel image, which yields a $108 \times 108$ cell feature map.
The gold standard (non-pyramid) R-CNN performance using the same non-fine-tuned CNN is 44.2\% mAP.
Our best result with Pyramid R-CNN is slightly worse, at 41.9\%.

To map a ROI $R$ into the pyramid, we start by computing an ``optimal'' scale defined by $\alpha^* = 227/\min(h,w)$, where $h$ and $w$ are image height and width of $R$.
We then find the nearest level in the pyramid: $l^* = \textrm{argmin}_l |\log(\alpha_l) - \log(\alpha^*)|$, where $\alpha_l$ is the scale factor for pyramid level $l$.
This procedure approximates the scale that R-CNN would use, since it operates on $227$ pixel inputs.

\begin{table}[ht]
\centering
\caption{
    Pyramid R-CNN design choices, vs mAP performance.
    We additionally show two best and two worst performing classes.
}\label{tab:prcnn}
\small{
\input{pyra_rcnn_table}
}
\end{table}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/dense_rcnn.pdf}
\caption{
Post R-CNN architecture: the whole image is fed through a CNN up to the highest pooling layer.
Regions are cropped from that layer at the best matching scale, resized, and classified.
}\label{fig:dense_rcnn}
\end{center}
\end{figure}

### 2014-08-11 related_work.tex
removing everything about p-rcnn; restructuring method section

@@
 
-The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} .
+The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014} .
 
-These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.
-All these method have a fixed strategy and are unable to adapt their computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.
+These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-BMVC-2014,Sermanet-ICLR-2014}, or deriving a CNN-based window sampling scheme \cite{Simonyan-ICLR-2014}.
 
 \paragraph{Cascaded detection}\label{cascaded-detection}
-Detection cascades \cite{Viola2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
-This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}.
-Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade} as well as a boosted cascade trained on CNN features \cite{Zou-CVPR-2014}.
+Detection cascades \cite{Viola-IJCV-2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers.
+This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip some evaluations \cite{Benbouzid-ICML-2012}.
+Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{Sun-CVPR-2013} as well as a boosted cascade trained on CNN features \cite{Zou-BMVC-2014}.
 While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.
@@
 \paragraph{Dynamic selection}\label{dynamic-selection}
-Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,dulac2014}.
-In particular, we combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.
+Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,DulacArnold-ICLR-2014}.

### 2014-08-11 voc2007_fig.tex
removing everything about p-rcnn; restructuring method section

\begin{figure}[ht]
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
    \caption{mAP vs. speed-up factor}\label{fig:speedup}
\end{subfigure}
\caption{
Results on the PASCAL VOC 2007 dataset.
(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
}\label{fig:voc2007_results}
\end{figure}

### 2014-08-11 copy_bibtex.sh

@@ -1,4 +1,4 @@
 #!/bin/bash
 # Copy the "NIPS" Mendeley group bibtex to this folder.
 
-cp /Users/sergeyk/Dropbox/Documents/Mendeley/NIPS14.bib sergeyk_nips14.bib
+cp /Users/sergeyk/Dropbox/Documents/Mendeley/library.bib sergeyk_library.bib

### 2014-08-11 nips_rebuttal_1262.txt
rebuttals submitted

@@
 We thank the reviewers for their thoughtful consideration.
-We feel that the reviewers underestimated the impact of the Cascaded CNN we report, and see the need for a more clear rhetorical focus on this contribution.
+We feel that the impact of our novel Cascaded CNN model was underestimated.
+If given the chance, we will build a clear rhetorical focus on this contribution.
+Our proposed method is conceptually distinct and orthogonal to the most recent speedups of such architectures reported, even after time of submission.
 

### 2014-12-15 abstract.tex
minor changes
integrating changes from thesis

--- 2014-06-06 abstract.tex
@@
 \begin{abstract}
-The recently introduced R-CNN object detection framework has excellent detection accuracy, but is slow, running at 10 seconds per image on a GPU.
-R-CNN is slow because it classifies roughly 2k regions of interest (ROIs) per image without sharing computation between them.
-We propose and evaluate two novel speed-ups for R-CNN.
-First, we re-order regions to process the most promising ones first using one of three ``fast features'': (1) region overlap statistics; (2) CNN pixel gradient statistics; and (3) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation.
-Second, we propose a novel \emph{Cascaded CNN} that adds a \emph{reject} option after each CNN layer, which yields fast but accurate classification.
-We achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.
+We propose methods for speeding up CNN-based detection approaches while maintaining their high accuracy: (1) a dynamic region selection method using novel quick-to-compute features; and (2) the Cascade CNN, which adds a reject option between expensive convolutional layers and allows the network to terminate some computation early.
+The Cascade CNN is applicable to most class-imbalanced prediction tasks.
+We evaluate our approach with respect to the R-CNN object detection system, and achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.
 \end{abstract}

### 2014-12-15 ccnn_anytime_fig.tex
integrating changes from thesis

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{ccnn-expanded-anytime.pdf}
\caption[Architecture of the proposed Anytime CNN.]{
The proposed Anytime CNN augments traditional networks with fully-connected prediction layers after every computationally-expensive layer.
All prediction layers feed into an Anytime combination layer that computes accuracy and back-propagates from cost-sensitive loss.
Compare this architecture to \autoref{fig:ccnn}.
}\label{fig:ccnn_anytime}
\end{center}
\end{figure}

### 2014-12-15 ccnn_fig.tex
integrating changes from thesis

@@
 \begin{center}
-\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
+\includegraphics[width=0.98\columnwidth]{figures/ccnn-expanded.pdf}
 \caption{
-The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
+The Cascade CNN has a Reject option after computationally expensive layers, implemented as a binary prediction for reject/keep (background/foreground for our detection task).
+The goal of the Reject layer is to maintain high recall while culling as much of the batch as possible, so that we can avoid doing as much convolution in the next layer.
 }\label{fig:ccnn}

### 2014-12-15 conclusion.tex
8 pages
integrating changes from thesis

--- 2014-05-29 conclusion.tex
@@
-\section{Conclusion}\label{conclusion}
+\section{Conclusion}
 
-{[}Standard stuff{]}
-
-\subsection{Future work}\label{future-work}
-
-\begin{itemize}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  ?
-\end{itemize}
+Even the most recent state-of-the-art CNN-based detection methods are computationally expensive.
+We first consider approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
+We show that basic strategies, such as simply reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.
+Our main contribution is the Cascade CNN model, which adds a novel Reject layer between convolutional layers in the architecture.
+C-CNN obtains an 8x speedup of the R-CNN detection method with only a 10\% degradation of state-of-the-art performance on PASCAL VOC detection.

### 2014-12-15 evaluation.tex
integrating changes from thesis

@@
 We evaluate on the VOC 2007 test set.
+The result plots and details are shown in \autoref{fig:voc2007_results} and \autoref{tab:ccnn_results}.
 
@@
 The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.
-
 The R-CNN software was used as available in June 2014.
@@
 Different images are proposed different numbers of regions.
-\autoref{fig:roi_hist_and_gradient} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
+\autoref{fig:roi_hist} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
 An additional parameter is the size of each batch of regions that goes through the CNN.
@@
 
-\subsection{Experiments}
+The experimental settings are
 \begin{description}
@@
   \item[Region Selection] \hfill \\
-  The region statistics feature from \autoref{sec:region} is always used.
+  The region statistics feature is always used.
   Additionally, we consider the Pixel Gradient feature, with \emph{setup time} of the gradient forward-back propagation of 20 ms.
 
-  \item[Cascaded CNN] \hfill \\
-  The Cascaded CNN model, as described in \autoref{sec:ccnn}.
+  \item[Cascade CNN] \hfill \\
+  The Cascade CNN model, as described in \autoref{sec:ccnn}.
   The first experiment (C-CNN) takes batches of regions in a random order.
@@
 Since the time to process a full batch with a non-cascaded CNN is 500 ms, there are no results for non-cascaded baselines at 300 ms.
-At this time, the Cascaded CNN without any region ordering is best.
+At this time, the Cascade CNN without any region ordering is best.
 A reason for why C-CNN with Region Selection is not as good at this point is that the region selection presents better region candidates, with fewer rejection opportunities, and thus has less coverage of the image.
-
 At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
 Both method are better than the baseline non-cascaded methods for this entire duration.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.52\linewidth]{figures/roi_hist.pdf}
-\hfill
-\includegraphics[width=0.4\linewidth]{figures/gradient.pdf}
-\caption{
-(left) Distribution of number of regions per image.
-(right) Example of the CNN gradient.
-}\label{fig:roi_hist_and_gradient}
-\end{figure}

### 2014-12-15 introduction.tex
integrating changes from thesis

@@
 The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
-While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (following a separate region generation step).
 
-In this paper, we investigate a novel approach for speeding up R-CNN and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
+In this paper, we investigate a novel approach for speeding CNN-based detection methods and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
 We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
 When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
-We also consider a variety of strong baselines for speeding up R-CNN.

### 2014-12-15 method.tex
integrating changes from thesis

@@
 We first consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
-We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.
 
@@
 For the first source of information, we consider statistics about ROI location and overlap with other regions.
-For each ROI, we compute: its normalized location, its scale($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).
-
+For each ROI, we compute: its normalized location, its scale ($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).
 This simple feature works suprisingly well for filtering regions to process first.
@@
 This feature corresponds to a kind of saliency map, giving an estimate of the importance of each pixel to the final classification of the image.
-
-Our method follows \cite{Simonyan-ICLR-2014} to the best of our knowledge.
+Our method is independently developed, but agrees with the concurrently published work of \cite{Simonyan-ICLR-2014} quite closely.
 Images are resized to square and classified with an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss.
@@
 At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.
-A couple of example images are shown in \autoref{fig:roi_hist_and_gradient}.
-
+A couple of example images are shown in \autoref{fig:gradient_examples}.
 We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
@@
 
-\subsection{Cascaded CNN}\label{sec:ccnn}
+\begin{figure}[ht]
+\centering
+\begin{minipage}{.45\textwidth}
+\centering
+    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
+    \caption{
+    Distribution of number of regions per image.
+    }\label{fig:roi_hist}
+\end{minipage}\hfill%
+\begin{minipage}{.45\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/gradient_backprop.pdf}
+    \caption[Explanation of the gradient back-propagation quick feature.]{
+    As a quick feature, we back-propagate the gradient from the top classification layer all the way to the input pixels.
+    This induces a kind of saliency map on the image, which is useful signal for selecting image sub-regions to classify with the CNN.
+    }\label{fig:gradient_examples}
+\end{minipage}
+\end{figure}
 
-Most ROIs that are scored in R-CNN do not contain any object of interest.
-It would be useful to quickly reject these regions, without expending the full amount of computation on them.
+\subsection{Cascade CNN}\label{sec:ccnn}
 
-The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
+Despite the intentions of the region-proposal mechanism \cite{Uijlings-IJCV-2013}, most ROIs that are scored in R-CNN do not contain any object of interest.
+As in the classic cascade of \cite{Viola-IJCV-2004}, it would be useful to quickly reject these regions, without expending the full amount of computation on them.
+The problem is that the deep neural network architecture is trained to always run all the way through.
+We need to introduce a new primitive to enable early termination.
+
+The Cascade CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
 Each reject layer is implemented as a fully-connected layer following a linear rectification, trained with dropout using logistic loss on foreground/background labels.
-We set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.
+We first train an AlexNet-architecture network \cite{Krizhevsky-NIPS-2012} on the ImageNet classification dataset.
+This network is augmented with the Reject layers, its loss replaced with a multi-label cross-entropy loss, and fine-tuning on the PASCAL VOC training set is performed until loss stop decreasing (roughly 50000 iterations).
+In training, all instances pass through all Reject layers.
+After training, we set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.
 

### 2014-12-15 related_work.tex
integrating changes from thesis

@@
 
-The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014} .
+The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014,He-ECCV-2014} .
 

### 2014-12-15 voc2007_fig.tex
integrating changes from thesis

@@
 \begin{figure}[ht]
+\begin{subfigure}[b]{\linewidth}
     \centering
-\begin{subfigure}[b]{0.52\linewidth}
-    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
-    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
-\end{subfigure}\hfill
-\begin{subfigure}[b]{0.45\linewidth}
-    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
-    \caption{mAP vs. speed-up factor}\label{fig:speedup}
+    \includegraphics[width=.75\linewidth]{figures/_apvst_final.pdf}
+    \caption{
+Plotting Mean AP vs. Time Allotted allows comparison performance at a given time budget.
+For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
+}\label{fig:apvst}
+\end{subfigure}
+\begin{subfigure}[b]{\linewidth}
+    \centering
+    \includegraphics[width=.75\linewidth]{figures/_speedup_final_abs.pdf}
+    \caption{
+Plotting mean AP vs. speed-up factor allows comparison of speed-ups at a given mAP point.
+For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
+}\label{fig:speedup}
 \end{subfigure}
 \caption{
-Results on the PASCAL VOC 2007 dataset.
-(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
-For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
-(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
-For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
+Results of the Cascade CNN and other Anytime methods on the PASCAL VOC 2007 dataset.
 }\label{fig:voc2007_results}
